### 2025-01-13 doc/paper.qmd
paper.qmd update

---
title: |
  | Audit market concentration in the EU:
  | Corporate Decision-Making and Quantitative Analysis - Assignment I\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging the Audit Analytics database on Transparency Report data, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization. The project replicates and extends findings from the European Commission’s 2024 report by analyzing and visualizing Big 4, CR4, and 10KAP audit firms’ market shares in the number of public interest entity statutory audits for 2021 across EU countries and at the EU level. The results include a detailed breakdown of market concentration trends, offering insights into the dominance of major audit firms across different jurisdictions. In doing so, the project documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and demonstrates how to structure a reproducible empirical research project. 
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

\pagebreak

# List of Abbreviations
\setlength{\parindent}{0em}
**CRSP**: Center for Research in Security Prices
**EC**: European Commission  
**EU**: European Union  
**IDE**: Integrated Development Environment  
**NCA**: National Competent Authority  
**PIE**: Public interest entity  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**UK**: United Kingdom   
**WRDS**: Wharton Research Data Services

\setlength{\parindent}{4em}

\pagebreak

# Introduction {#sec-introduction}
The aim of this paper is to illustrate the use of open science tools in empirical accounting research.

The original report by @EC_Report_2024 examines trends in the European Union (EU) market for statutory audits of public interest entities (PIEs) from 2019 to 2021, with a focus on market concentration, audit quality risks, and the effectiveness of audit committees. This report is the third check-in on how the EU’s auditing standards and market structures are evolving since the *Article 27 of Regulation (EU) No 537/2014* [-@EU_Regulation_537_2014] was introduced, which introduces a host of specific audit requirements for PIEs. A statutory audit is a legally mandated evaluation of financial records aimed at certifying the accuracy of companies’ financial statements, thereby enhancing stakeholder confidence and supporting the orderly functioning of markets [@EC_Auditing_Website]. The report by @EC_Report_2024 argues that while statutory audits play a crucial role in fostering confidence in financial markets, persistent market concentration and quality deficiencies highlight the need for strengthened oversight and improved transparency to ensure the resilience and reliability of audit practices across the EU.

This paper replicates Figure 3 from the European Commission’s [-@EC_Report_2024] report, which visualizes the market shares of audit firms — Big 4, CR4, and 10KAP — by the number of PIE statutory audits conducted in 2021 across EU countries and at the EU level. The replication provides insights into market concentration and the dominance of major audit firms, reflecting variations in audit practices and competition across Europe.

The project uses data from the Audit Analytics database on Transparency Reports via Wharton Research Data Services (WRDS) for the year 2021, covering PIEs across EU countries. The replication closely follows the methodology outlined by @EC_Report_2024. It focuses on three key market concentration measures: the market share of the Big 4 audit firms, the CR4 market share for the largest four firms in each country, and the 10KAP market share, which includes the Big 4 and additional major networks. These measures provide a detailed assessment of audit firm dominance and competition, offering valuable insights into the structure and dynamics of the statutory audit market in Europe.

The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level. Explicit assumptions were made whenever the document by @EC_Report_2024 was unclear on how to proceed. The entire Python computation code for market share calculations is available in `code/python/do_analysis.py` for detailed review if necessary. This paper focuses on the replication process, presenting visualizations, and discussing the results.

The replicated figure from original report by @EC_Report_2024 is shown below, followed by the research design choices and assumptions in @sec-research_design_assumptions, documentation of the replication steps in @sec-replication_steps, a detailed results comparison in @sec-results, and concluding remarks in @sec-conclusion.

@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021. Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. The discussion of replication findings is presented in @sec-results.
```{python}
#| label: fig-market-shares
#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
#| fig-align: center
#| echo: false

import pickle
import matplotlib.pyplot as plt

# Load the figure from the pickle file
with open('../output/figure3_market_shares.pickle', 'rb') as f:
    fig = pickle.load(f)

# Render the figure explicitly
plt.figure(fig.number)
plt.show()
```

# Research Design Choices and Assumptions {#sec-research_design_assumptions}
The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024. This figure involves analyzing the market shares of audit firms (Big 4, CR4, and 10KAP) across EU countries and at the EU level for PIE statutory audits conducted in 2021. The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures. For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis. The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].

Following @EC_Report_2024, I focus the analysis on statutory audits conducted for the fiscal year 2021, ensuring that the data accurately reflects the audit market structure in the EU as specified in the original report. The replication aims to mirror the research design as closely as possible with the available data.

In addition, I impose the following assumptions to ensure clarity and consistency where the report by @EC_Report_2024 does not provide explicit guidance:

1.	The original report references the reports prepared by national competent authorities (NCAs) responsible for audit oversight as the main source of data, where the data refers to the years 2020 and 2021 and was collected in 2022 [@EC_Report_2024, p.1]. However, this replication uses data obtained from the Audit Analytics Transparency Reports database via WRDS, which provides the latest available version as of September 2024, updated quarterly [@WRDS_Audit_Analytics_Transparency_Reports]. Due to potential adjustments and updates made to the database since the original data collection period, there may be differences that could affect the results. For example, audit firms may disclose updated information in subsequent reports, which would be reflected in the later database version rather than the historical snapshot used in the original report. Furthermore, the data vendor regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the 2022 snapshot.
2.	The original paper outlines key terms that will be used in this project to ensure consistency and accuracy in the replication. @EC_Report_2024 defines the 'Big Four' as Deloitte, EY, KPMG, and PwC; the 'CR4' as the four largest audit firms in each country; and the '10KAP' as a group consisting of Baker Tilly, BDO, Deloitte, EY, Grant Thornton, KPMG, Mazars, Nexia, RSM, and PwC. 
3.	As for the geographical scope, I use the variable `trans_report_auditor_state` to identify the country associated with each audit firm rather than the audited company’s headquarter country (`headquarter_country` variable). Since the objective is to analyze audit market concentration and the market share of audit firms within specific countries, the country of the audit firm’s reported activity is more relevant than the headquarter country of the entities they audit.
4.	Another potential source of discrepancies between the original and replicated tables may be the choice of variables pulled from Audit Analytics. For example, in the `audit_europe.feed76_transparency_reports` table, I chose `entity_map_fkey` over `entity_map_key`, as this unique identifier is created by WRDS for merging [@WRDS_Audit_Analytics_Transparency_Reports]. Since the report does not specify the choice of variables used from the database, this could cause differences in the results.
5.	For the purpose of replicating Figure 3, I use the `report_year` variable as the primary filter to define the relevant data for year 2021. This choice is based on the fact that `report_year` represents the idealized fiscal year of the Transparency Report, based on the *Europe Transparency Reports Data Dictionary* by Wharton Research Data Services [-@Europe_Transparency_Reports_Data_Dictionary], which aligns directly with the year-based aggregation needed for Figure 3. While the `report_period_end_date` provides the exact end date of each reporting period [@Europe_Transparency_Reports_Data_Dictionary], using `report_year` allows for a consistent, annual aggregation without requiring additional alignment of various period end dates. This approach simplifies the data extraction and ensures that all entries correspond to the fiscal year 2021.

By following the steps provided in @sec-replication_steps and adhering to the assumptions made, I successfully replicated the analysis and produced the required figure. A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.

# Replication Steps {#sec-replication_steps}

## Step 1: Pulling the Data and Managing the Database
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

To ensure data relevance, the pulling process was restricted to data for the year 2021. The variable `trans_report_auditor_state` was used to filter the data to include only audit firms associated with the specific EU and EEA countries, as specified in configuration file `config/pull_data_cfg​`. This filtering step ensured that the analysis focuses on audit market concentration within the geographical scope and year range as defined by @EC_Report_2024.

## Step 2: Data Preparation {#sec-step2_preparation}
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

The `number_of_disclosed_pies` variable provides the clearest indication of statutory audits conducted by each auditor for PIEs. The definition of PIEs varies across EU and EEA countries [@AccountancyEurope_PIE_2017], but if Transparency Reports consistently follow country-specific definitions, using the provided variable is reasonable. An important verification step involved comparing the reported `number_of_disclosed_pies` with the count of unique `entity_map_fkey` entries for each `transparency_report_fkey`. This analysis revealed that 5,696 transparency reports included fewer entities in the dataset than the disclosed PIEs, suggesting that some PIE entities might be missing from the dataset. This discrepancy reflects missing PIE data rather than the inclusion of non-PIE entities, hence it is assumed that all entities in the dataset are PIEs, maintaining consistency in the framework for analysis.

Additionally, missing values in key fields, including `transparency_report_fkey`, `entity_map_fkey`, `auditor_fkey`, and `trans_report_auditor_state`, were checked, and it was confirmed that no rows needed to be removed due to missing data, ensuring the completeness of the dataset. To focus on relevant data, rows with `number_of_disclosed_pies` equal to or less than zero were filtered, but no such rows were identified, and all observations were retained.

Duplicate entries in the `entity_map_fkey` column were then analyzed, revealing 1,011 duplicate entities. I assume that duplicate entries in the dataset do not introduce significant issues for the replication of Figure 3. Duplicate entries for the same entity are expected in cases where an entity is audited by multiple audit firms or networks, potentially as part of a joint audit. Since these duplicates retain consistent information on `trans_report_auditor_state`, they do not distort country-level distributions. Additionally, while duplicates might expand representation across different auditor networks or groups, the essence of Figure 3 — focusing on aggregate distributions — remains unaffected. Therefore, these duplicates were not removed.

Auditor network names were standardized to ensure consistency, with names like `|Mazars Worldwide|Praxity Global Alliance|` simplified to `|Mazars Worldwide|`, for example. This standardization helped avoid double-counting and unify same entries under consistent naming conventions.

Audit firms were then categorized into groups, including the Big 4 (Deloitte, EY, KPMG, and PwC), the 10KAP (which includes the Big 4 along with other major networks listed in @sec-research_design_assumptions), 'Unaffiliated' firms (those outside the Big 4 and 10KAP). The `auditor_network` field contained 636 observations with missing values, which were grouped under the “Other (Blank)” category. I assume that these blank entries do not belong to the Big Four or 10KAP networks but may still contribute to the CR4 category in some countries. So, these entries were retained in the dataset and reviewed during the aggregation stage to validate their relevance.

These preparation steps ensured alignment with the methodology of @EC_Report_2024 and the dataset’s readiness for subsequent analysis.

## Step 3: Analysis Implementation and Figure Reproduction
The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data. The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021. For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts. The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.

The following formula is used to calculate market share:
$$
\text{Market Share (\%)} = \left( \frac{\text{Number of PIE Audits by Network Group}}{\text{Total PIE Audits in Country}} \right) \times 100
$$

The analysis also includes the creation of a bar chart visualizing market shares for all countries and the EU aggregate, saved in both PNG and pickle formats. The aggregated market share data is saved in CSV format, ensuring reproducibility and further analysis opportunities.

# Results {#sec-results}
To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`. The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance. Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries. For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets. However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions. The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries. This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.

The inclusion of additional audit networks through the 10KAP grouping increases the market share substantially across all countries, as expected. This is particularly evident in countries like Ireland, Malta, and the Netherlands, where the 10KAP share reaches 100%, reflecting the full inclusion of statutory audits under this grouping. In contrast, countries like Bulgaria and Poland, with 10KAP shares of 41.8% and 63.6%, respectively, suggest the presence of a substantial number of statutory audits conducted by unaffiliated or smaller firms.

In the analysis of CR4 market shares, I verified whether the four largest audit firms (CR4) in each country overlapped entirely with the Big 4 audit firms. This overlap occurred in 15 out of 28 countries, where CR4 and Big 4 market shares were identical. In the remaining 13 countries, at least one non-Big 4 firm contributed significantly to the statutory audits, resulting in distinct CR4 market shares. These findings align with @EC_Report_2024, which notes that in 13 Member States, the Big Four are not the four largest audit firms in terms of the total number of PIE statutory audit opinions. This highlights the gradual diversification in the audit market in some countries, where non-Big 4 firms are playing a more prominent role, while the Big 4 continue to dominate in others.

At the EU level, the aggregated market shares further underscore the dominance of these major players. The Big 4 account for 70% of statutory audits, compared to @EC_Report_2024, which notes an average EU market share of 59% for the Big 4 in 2021, down from 70% in 2018. The broader 10KAP grouping in my output reaches nearly 90%, exceeding the 81% reported by @EC_Report_2024. The CR4 market share at the EU level also stands at 70%, aligning with the Big 4, and is consistent with the average CR4 market share reported by @EC_Report_2024. These results highlight the varying degrees of market concentration across Europe, with certain countries demonstrating a highly centralized audit market dominated by the Big 4, while others display a more distributed market landscape, incorporating both major and smaller audit firms. The slight discrepancies in the figures suggest potential differences in methodologies, data coverage, or sample definitions.

Based on the results for Austria, the Big 4 market share is 86.7% in my analysis, aligning closely with the approximate 85% represented in bar chart of @EC_Report_2024. Similarly, the 10KAP market share of 92.55% in my analysis corresponds well with the slightly higher bar in the report, and the CR4 market share of 86.7% aligns perfectly with the Big 4 share, confirming the dominance of these firms in Austria’s audit market. This consistency highlights the robustness of the replicated analysis for this country.

The results for Romania show notable discrepancies. The EC Report indicates market shares of 15% for the Big 4, 16% for CR4, and 24% for 10KAP, while my analysis reports significantly higher values: 63%, 70.61%, and 78.38%, respectively. These differences likely arise from assumptions made in @sec-research_design_assumptions like variations in PIE definitions and auditor classifications. The report by @EC_Report_2024 may use stricter criteria, reflecting Romania’s decentralized market where non-Big 4 firms dominate, unlike the broader inclusion in my dataset.

In summary, the replication effectively captures the original report's key findings, confirming the dominance of the Big 4 and the broader 10KAP group in the European audit market. The analysis highlights varying degrees of market concentration across countries, with some demonstrating a more decentralized audit landscape. While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.

# Conclusion {#sec-conclusion}
The project effectively demonstrates the use of a systematic and collaborative workflow for analyzing audit market concentration across Europe, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research. By following a structured approach, I successfully replicated a key figure and empirical findings of @EC_Report_2024, offering insights into the dominance of the Big 4 and the broader 10KAP group in the European audit market.

This assignment is an exact replication of the report by @EC_Report_2024, where the goal was to closely follow the report’s approach wherever possible and make justified assumptions when necessary. While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process.

The analysis reveals significant variation in market concentration across countries, with the Big 4 accounting for over 80% of market share in 11 countries, while others show a more decentralized landscape where non-Big 4 firms contribute substantially. These findings align closely with the original study results, confirming the reliability of the data and methodologies used in this replication. However, discrepancies in specific countries, such as Romania, highlight the importance of transparent methodologies and consistent definitions when conducting such analyses.

This assignment required a comprehensive application of skills learned throughout the course, incorporating data analysis, replication techniques, and visualization. In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis. Thanks for reading!

\pagebreak

\setcounter{table}{0}
\renewcommand{\thetable}{\arabic{table}}

# References {-}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent

### 2025-01-14 doc/paper.qmd
paper&readme update

@@
 title: |
-  | Audit market concentration in the EU:
-  | Corporate Decision-Making and Quantitative Analysis - Assignment I\vspace{1cm}
+  | How Much New Information Is There in Earnings?
+  | Corporate Decision-Making and Quantitative Analysis - 
+  | Individual Report\vspace{1cm}
 author:

### 2025-01-14 doc/paper.qmd
Intergrated Zotero Quick Copy for BibTeX references

@@
 
-This assignment required a comprehensive application of skills learned throughout the course, incorporating data analysis, replication techniques, and visualization.
+This assignment required a comprehensive application of programming skills and institutional knowledge gained throughout the course, integrating data analysis, replication, and visualization techniques in line with open science principles.
 In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis.

### 2025-01-15 doc/paper.qmd
abstract update

@@
   | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects.
-Leveraging the Audit Analytics database on Transparency Report data, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization.
-The project replicates and extends findings from the European Commission’s 2024 report by analyzing and visualizing Big 4, CR4, and 10KAP audit firms’ market shares in the number of public interest entity statutory audits for 2021 across EU countries and at the EU level.
-The results include a detailed breakdown of market concentration trends, offering insights into the dominance of major audit firms across different jurisdictions.
-In doing so, the project documents and discusses the research design choices made and the variations between the original and reproduced results.
+Leveraging data from the CRSP and Compustat databases via WRDS alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization.
+The project replicates and extends findings from Ball and Shivakumar (2008) by analyzing the informativeness of quarterly earnings announcements and their contribution to annual share price movements.
+Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S.
+country.
+In doing so, the project documents and discusses the research design choices made and the variations between the original anf reproduced results.
+The results offer insights into the informational value of earnings announcements across different timeframes and jurisdictions.
+Additionally, the project sketches a research design for a non-archival study to evaluate the paper’s findings.
 This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and demonstrates how to structure a reproducible empirical research project.

### 2025-01-15 doc/paper.qmd
readme adjust

@@
   | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects.
-Leveraging data from the CRSP and Compustat databases via WRDS alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization.
+Leveraging data from the CRSP and Compustat databases via WRDS, alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization.
 The project replicates and extends findings from Ball and Shivakumar (2008) by analyzing the informativeness of quarterly earnings announcements and their contribution to annual share price movements.
@@
 country.
-In doing so, the project documents and discusses the research design choices made and the variations between the original anf reproduced results.
+In doing so, the project documents and discusses the research design choices made and the variations between the original and reproduced results.
 The results offer insights into the informational value of earnings announcements across different timeframes and jurisdictions.

### 2025-01-16 doc/paper.qmd
readme finished
read

@@
 Leveraging data from the CRSP and Compustat databases via WRDS, alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization.
-The project replicates and extends findings from Ball and Shivakumar (2008) by analyzing the informativeness of quarterly earnings announcements and their contribution to annual share price movements.
+The integration of multiple databases adds a higher layer of complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze the data effectively.
+The project replicates and extends findings from Ball and Shivakumar (2008) to analyze the informativeness of quarterly earnings announcements and their contribution to annual share price movements, highlighting their essential role in investment decisions and their impact on investors, analysts, and policymakers.
 Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S.

### 2025-01-16 doc/paper.qmd
abstract finished

--- 2025-01-15 doc/paper.qmd
@@
 abstract: |
-  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects.
-Leveraging data from the CRSP and Compustat databases via WRDS alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization.
-The project replicates and extends findings from Ball and Shivakumar (2008) by analyzing the informativeness of quarterly earnings announcements and their contribution to annual share price movements.
-Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S.
+  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide infrastructure for open science-oriented empirical projects.
+Leveraging data from the CRSP and Compustat databases via WRDS, alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow integrating Python scripts for data preparation, analysis, and visualization.
+Integrating multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
+The project replicates and extends Ball and Shivakumar (2008) to analyze the informativeness of quarterly earnings announcements and their contribution to annual share price movements, highlighting their critical role in investment decisions and impact on investors, analysts, and policymakers.
+Key tasks include replicating and comparing original results, extending the analysis to 2007–2023, and applying the methodology to a non-U.S.
 country.
-In doing so, the project documents and discusses the research design choices made and the variations between the original anf reproduced results.
-The results offer insights into the informational value of earnings announcements across different timeframes and jurisdictions.
-Additionally, the project sketches a research design for a non-archival study to evaluate the paper’s findings.
-This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and demonstrates how to structure a reproducible empirical research project.
-  | \vspace{6cm}
+The project also documents research design choices, discusses variations between original and reproduced results, and provides insights into earnings informativeness across different timeframes and jurisdictions.
+Additionally, it sketches a research design for a non-archival study to evaluate the paper’s findings.
+This code base, adapted from TREAT, demonstrates how the template applies to this project and serves as a structured guide for reproducible empirical research in accounting.
+  <!--
+  | \vspace{6cm} commenting away to decrease distance
+  -->
+
 bibliography: references.bib

### 2025-01-20 doc/paper.qmd
added list of tables and figures (for better navigation)

@@
     toc: true
+    lof: true  # Enables List of Figures
+    lot: true  # Enables List of Tables
 fig_caption: yes
@@
 **IDE**: Integrated Development Environment  
-**NCA**: National Competent Authority  
-**PIE**: Public interest entity  
 **TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  

### 2025-01-20 doc/paper.qmd
Introduction and Conclusion finished

@@
 date: today
-date-format: MMM D, YYYY [\vspace{1cm}]
+date-format: MMM D, YYYY [\vspace{0cm}] # Adjust the vertical space after the date from 1cm
 abstract: |
@@
 **CRSP**: Center for Research in Security Prices  
+**CQA**: Corporate Decision-Making and Quantitative Analysis  
 **EC**: European Commission  
@@
 The aim of this paper is to illustrate the use of open science tools in empirical accounting research.
+This project builds on the methodological framework established in the Corporate Decision-Making and Quantitative Analysis (CQA) course, which explored a range of empirical research methods—including archival analysis, field experiments, and survey-based approaches—to develop a comprehensive understanding of corporate decision-making and quantitative analysis.
+Expanding on prior empirical research conducted in Assignments I and II, this paper extends the empirical focus of the course.
+Assignment I examined audit market concentration in the EU using Transparency Reports data, offering insights into the dominance of major audit firms and the structure of the European audit market.
+Assignment II explored the economic implications of corporate financial reporting, focusing on @graham_economic_2005 to analyze managerial decision-making, earnings management strategies, and voluntary disclosure practices.
+This study highlighted the trade-offs between short-term earnings predictability and long-term firm value and provided a foundation for understanding corporate incentives in financial reporting.
 
-The original report by @EC_Report_2024 examines trends in the European Union (EU) market for statutory audits of public interest entities (PIEs) from 2019 to 2021, with a focus on market concentration, audit quality risks, and the effectiveness of audit committees.
-This report is the third check-in on how the EU’s auditing standards and market structures are evolving since the *Article 27 of Regulation (EU) No 537/2014* [-@EU_Regulation_537_2014] was introduced, which introduces a host of specific audit requirements for PIEs.
-A statutory audit is a legally mandated evaluation of financial records aimed at certifying the accuracy of companies’ financial statements, thereby enhancing stakeholder confidence and supporting the orderly functioning of markets [@EC_Auditing_Website].
-The report by @EC_Report_2024 argues that while statutory audits play a crucial role in fostering confidence in financial markets, persistent market concentration and quality deficiencies highlight the need for strengthened oversight and improved transparency to ensure the resilience and reliability of audit practices across the EU.
+Building on these foundations, Assignment III investigates the informativeness of quarterly earnings announcements and their contribution to annual share price movements.
+The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets.
+By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency.
+The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
+Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S.
+country to explore cross-market variations.
+
+Beyond empirical replication, the project also documents research design choices, replication steps, and explicit assumptions made whenever the original paper was unclear on how to proceed.
+It discusses variations between original and reproduced results and provides insights into the timeliness and market impact of earnings announcements across different timeframes and jurisdictions.
+Additionally, it sketches a research design for a non-archival study to evaluate the paper’s findings through an alternative methodological lens.
+This project leverages the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to establish an open science-oriented infrastructure, ensuring transparency, replicability, and structured workflows for empirical accounting research.
+
+Earnings announcements provide investors with valuable information about a firm’s market value, with stock prices reacting significantly when earnings news deviates from expectations [@fink_review_2021, p.2].
+The seminal study by @ball_empirical_1968 was the first to document this relationship, and over the past decades, more than a thousand studies have examined the interplay between capital markets and financial statements, a research stream that originated with Ball and Brown (1968) [@kothari_capital_2001].
+This reinforces the role of earnings announcements as a crucial source of financial information.
+
+Building on this foundation, the original study by @ball_how_2008 investigates the extent to which quarterly earnings announcements contribute new information to the market, assessing their role in shaping annual share price movements.
+By estimating the R² from regressions of annual stock returns on earnings announcement window returns, the paper quantifies the informativeness of earnings releases, finding that they account for only 1% to 2% of total annual volatility.
+This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights.
+The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.
+
+While @ball_how_2008 provide key insights into the informativeness of earnings announcements, their study was conducted within a specific timeframe and market context.
+Since then, financial markets have undergone significant changes due to regulatory reforms, economic crises, and technological advancements in financial information processing.
+Moreover, the extent to which earnings informativeness varies across international markets remains underexplored.
+By replicating their study with updated data from 2007–2023 and applying the methodology to a non-U.S.
+country, this project reassesses the robustness of their findings, examines long-term trends, and evaluates cross-country differences in earnings informativeness.
+Through this approach, it critically evaluates the generalizability of the original results and provides further insights into the economic role of earnings announcements in financial markets, offering a contemporary perspective on their evolving informativeness and implications for investors, analysts, and policymakers.
+
+The paper is structured into sections corresponding to Tasks 1–4, where each section presents the research design choices and assumptions, documents the replication steps, and analyzes the replication results.
+The concluding remarks are provided in @sec-conclusion.
+
+# Task 1 {#sec-task1}
 
@@
 
-# Research Design Choices and Assumptions {#sec-research_design_assumptions}
+## Research Design Choices and Assumptions - Task 1 {#sec-research_design_assumptions1}
 The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024.
@@
 
-# Replication Steps {#sec-replication_steps}
+## Replication Steps - Task 1 {#sec-replication_steps1}
 
-## Step 1: Pulling the Data and Managing the Database
+### Step 1: Pulling the Data and Managing the Database
 This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.
@@
 
-## Step 2: Data Preparation {#sec-step2_preparation}
+### Step 2: Data Preparation {#sec-step2_preparation}
 The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021.
@@
 
-## Step 3: Analysis Implementation and Figure Reproduction
+### Step 3: Analysis Implementation and Figure Reproduction
 The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data.
@@
 
-# Results {#sec-results}
+## Results - Task 1 {#sec-results}
 To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`.
@@
 # Conclusion {#sec-conclusion}
-The project effectively demonstrates the use of a systematic and collaborative workflow for analyzing audit market concentration across Europe, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research.
-By following a structured approach, I successfully replicated a key figure and empirical findings of @EC_Report_2024, offering insights into the dominance of the Big 4 and the broader 10KAP group in the European audit market.
+This project effectively demonstrates the use of a systematic and collaborative workflow for empirical accounting research, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research.
+By following an open science approach, I successfully replicated key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency.
+While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process.
+Moreover, by extending the analysis beyond the original study’s U.S.
+market focus, the project highlights how market structures and investor behaviors influence the informativeness of earnings disclosures in different jurisdictions.
 
-This assignment is an exact replication of the report by @EC_Report_2024, where the goal was to closely follow the report’s approach wherever possible and make justified assumptions when necessary.
-While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process.
-
-The analysis reveals significant variation in market concentration across countries, with the Big 4 accounting for over 80% of market share in 11 countries, while others show a more decentralized landscape where non-Big 4 firms contribute substantially.
-These findings align closely with the original study results, confirming the reliability of the data and methodologies used in this replication.
-However, discrepancies in specific countries, such as Romania, highlight the importance of transparent methodologies and consistent definitions when conducting such analyses.
+The study contributes to the ongoing discussion on market efficiency and the economic role of corporate disclosures by providing empirical evidence on how earnings informativeness has evolved over time and across jurisdictions.
+The cross-country analysis highlights variations in market responses to earnings announcements, suggesting that institutional factors, market structures, and investor behavior play a role in shaping how financial information is processed.
+These findings have implications for investors, analysts, and policymakers, as they underscore the importance of regulatory consistency and market transparency in shaping the effectiveness of financial reporting.
 
 This assignment required a comprehensive application of programming skills and institutional knowledge gained throughout the course, integrating data analysis, replication, and visualization techniques in line with open science principles.
-In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis.
+In the future, this repository can be cloned or forked (if made public) to facilitate further research on earnings informativeness, enabling additional extensions or robustness tests.
+Additionally, the survey developed as part of the non-archival study proposal can be further refined and expanded, providing a structured framework for gathering primary data on market participants’ interpretations of earnings announcements.
+Through this approach, the study not only revisits a fundamental question in financial research but also provides a foundation for future empirical investigations into the evolving role of earnings announcements in global capital markets, both through archival and non-archival methodologies.
 Thanks for reading!

### 2025-01-21 doc/paper.qmd
streamlined paper outline

@@
 
-The paper is structured into sections corresponding to Tasks 1–4, where each section presents the research design choices and assumptions, documents the replication steps, and analyzes the replication results.
+The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment.
+@sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper.
 The concluding remarks are provided in @sec-conclusion.
@@
 
-### Step 1: Pulling the Data and Managing the Database
+  Step 1: Pulling the Data and Managing the Database
 This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.
@@
 
-### Step 2: Data Preparation {#sec-step2_preparation}
+  Step 2: Data Preparation {#sec-step2_preparation}
 The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021.
@@
 
-### Step 3: Analysis Implementation and Figure Reproduction
+  Step 3: Analysis Implementation and Figure Reproduction
 The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data.
@@
 
+# Task 2 {#sec-task2}
+
+# Task 3 {#sec-task3}
+
+# Task 4 {#sec-task4}
+
 # Conclusion {#sec-conclusion}

### 2025-01-22 doc/paper.qmd
revised section names

@@
 **CQA**: Corporate Decision-Making and Quantitative Analysis  
-**EC**: European Commission  
-**EU**: European Union  
+**DV**: Dependent Variable
+**IV**: Independent Variable
+**EU**: European Union  ##
 **IDE**: Integrated Development Environment  
 **TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
-**UK**: United Kingdom  
+**UK**: United Kingdom  ##
 **WRDS**: Wharton Research Data Services
@@
 The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets.
-By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency.
+By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting.
 The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
@@
 Earnings announcements provide investors with valuable information about a firm’s market value, with stock prices reacting significantly when earnings news deviates from expectations [@fink_review_2021, p.2].
-The seminal study by @ball_empirical_1968 was the first to document this relationship, and over the past decades, more than a thousand studies have examined the interplay between capital markets and financial statements, a research stream that originated with Ball and Brown (1968) [@kothari_capital_2001].
+The seminal study by @ball_empirical_1968 was the first to document this relationship, showing that stock prices anticipate earnings surprises, with most of the market reaction occurring before the official announcement, suggesting that earnings reports primarily confirm rather than introduce new information.
+Over the past decades, more than a thousand studies have examined the interplay between capital markets and financial statements, a research stream that originated with Ball and Brown (1968)  [@kothari_capital_2001].
 This reinforces the role of earnings announcements as a crucial source of financial information.
@@
 
-# Task 1 {#sec-task1}
+# Task 1 - Replication of Key Tables and Figures {#sec-task1}
 
@@
 
-# Task 2 {#sec-task2}
+# Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}
 
-# Task 3 {#sec-task3}
+# Task 3 - Cross-Country Replication {#sec-task3}
 
-# Task 4 {#sec-task4}
+# Task 4 - Research Design for a Non-Archival Study {#sec-task4}
 

### 2025-01-22 doc/paper.qmd
Task 4 complete

@@
 **DV**: Dependent Variable
+**HU**: Humboldt-Universität zu Berlin
 **IV**: Independent Variable
@@
 
+The research design follows the generalization goal in empirical literature, emphasizing the need to validate findings across different methods [@bloomfield_gathering_2016].
+@ball_how_2008 assess earnings informativeness through stock price reactions, but triangulation—beyond replication—requires diverse methods to examine the same question [@bloomfield_gathering_2016, p.353].
+While price reactions indicate market response, they do not capture investor perceptions.
+A survey directly evaluates whether market participants view earnings announcements as confirmatory or informative.
+If investors confirm a secondary role, it reinforces Ball and Shivakumar’s (2008) findings, ensuring informativeness reflects cognitive and behavioral mechanisms rather than price fluctuations.
+These insights could inform corporate reporting strategies by clarifying how investors prioritize disclosures.
+
+A survey is the most suitable non-archival method, capturing investor sentiment beyond what archival data provides.
+Unlike lab experiments, which lack real-world applicability, surveys measure the dependent variable (DV) by eliciting participant perceptions [@bloomfield_gathering_2016, p.358].
+Field experiments, though capturing real-time reactions, require direct intervention, posing ethical and logistical challenges.
+A long-term research program combining surveys and field studies would enhance validity, leveraging unlimited funds to assess investor decision-making and market responses.
+
+To ensure survey reliability, design strategies follow @bruggemann_worku_2024.
+A sample of 300 investors, analysts, and financial professionals will provide institutional and retail perspectives while balancing statistical power and feasibility.
+The survey will be distributed via email through financial networks, investor associations, and professional platforms (e.g., LinkedIn, CFA societies) and in paper format at finance conferences.
+The Humboldt-Universität zu Berlin (HU) brand may be used, subject to approval.
+Respondents will be assured confidentiality and offered an €20 honorarium.
+A pilot study with 30 participants will refine question clarity, survey length, and response distribution, helping identify unclear or missing questions and assess completion time.
+
+To minimize response bias, questions will be neutrally worded to capture pre- and post-announcement perceptions.
+The fully anonymous survey ensures candid responses without requiring personal financial history.
+
+The **DV** is the perceived informativeness of earnings announcements, measured through survey responses on whether they are confirmatory or informative.
+Independent variables (**IVs**) include investor preparation, market awareness, reaction timing, perceived novelty of earnings, key financial indicators, and external conditions.
+These are measured via Likert-scale, ranking, and multiple-choice questions, supplemented by qualitative insights from follow-up interviews.
+
+To deepen findings, selected participants will be invited for confidential follow-up interviews, ensuring diversity in investment strategies, industries, and expertise.
+These interviews will be conducted via video conferencing or phone calls.
+The following sections provide detailed sketches of the survey and interview designs.
+
+## Survey Questions
+
+1. **How do you typically prepare for earnings announcements in your investment decisions?**
+    * I conduct in-depth research and adjust my positions in advance 
+    * I monitor but rarely adjust positions pre-announcement
+    * I rely on market consensus, analyst forecasts, and AI-driven insights
+    * I do not make investment decisions based on earnings announcements
+
+2. **How do you typically react to earnings announcements?**
+    * I adjust my investment strategy immediately based on the announcement.
+    * I wait for further analysis before making changes.
+    * I rarely make investment decisions based on earnings announcements.
+
+3. **To what extent do you believe that earnings announcements provide new information beyond what is already reflected in market prices?**
+    * Always
+    * Most of the time
+    * Sometimes
+    * Rarely
+    * Never
+
+4. **Rank the following factors in order of importance when evaluating earnings announcements (i = most important, v = least important):**
+    i) Earnings per share (EPS) compared to analyst forecasts
+    ii) Revenue growth
+    iii) Management guidance and commentary
+    iv) Market reaction on the day of the announcement
+    v) Industry trends and macroeconomic conditions
+
+5. **Do you consider earnings announcements to be more confirmatory or informative?**
+    * Primarily confirmatory (reinforce existing expectations)
+    * Primarily informative (provide new insights)
+    * A mix of both
+
+## Follow-Up Interview Questions
+
+1. Can you describe a recent instance where an earnings announcement significantly influenced your investment decision?
+2. In your experience, are there specific industries where earnings announcements are more informative than confirmatory?
+3. Do you use earnings announcements differently depending on market conditions (e.g., economic downturn vs. growth periods)?
+
 # Conclusion {#sec-conclusion}

### 2025-01-22 doc/paper.qmd
Added structured subsections

@@
 
-## Research Design Choices and Assumptions - Task 1 {#sec-research_design_assumptions1}
+## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
 The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024.
@@
 
-## Replication Steps - Task 1 {#sec-replication_steps1}
+## Replication Steps {#sec-replication_steps1}
 
@@
 
-## Results - Task 1 {#sec-results}
+## Results {#sec-results1}
 To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`.
@@
 # Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}
+## Research Design Choices and Assumptions {#sec-research_design_assumptions2}
+## Replication Steps {#sec-replication_steps2}
+## Results {#sec-results2}
 
 # Task 3 - Cross-Country Replication {#sec-task3}
+## Research Design Choices and Assumptions {#sec-research_design_assumptions3}
+## Replication Steps {#sec-replication_steps3}
+## Results {#sec-results3}
 

### 2025-01-22 doc/paper.qmd
refinement

@@
 
-4. **Rank the following factors in order of importance when evaluating earnings announcements (i = most important, v = least important):**
-    i) Earnings per share (EPS) compared to analyst forecasts
-    ii) Revenue growth
-    iii) Management guidance and commentary
-    iv) Market reaction on the day of the announcement
-    v) Industry trends and macroeconomic conditions
+4. **Rank the following factors in order of importance when evaluating earnings announcements (1 = most important, 5 = least important):**
+    * Earnings per share (EPS) compared to analyst forecasts
+    * Revenue growth
+    * Management guidance and commentary
+    * Market reaction on the day of the announcement
+    * Industry trends and macroeconomic conditions
 

### 2025-01-23 doc/paper.qmd
minor refine

@@
 date: today
-date-format: MMM D, YYYY [\vspace{0cm}] # Adjust the vertical space after the date from 1cm
+date-format: MMM D, YYYY [\vspace{0cm}] # Adjusted the vertical space after the date from 1cm
 abstract: |

### 2025-01-23 code/python/do_analysis.py
following feedback advice for analysis.py + readme upd

@@ -264,7 +264,13 @@ def plot_market_shares(market_shares, save_path, pickle_path):
         pickle.dump(fig, f)
     log.info(f"Figure saved as pickle to {pickle_path}.")
     
-    plt.show()
+    #plt.show() 
+    """
+    as advised by feedback - One minor thing that you should not do, is `plt.show()` in your final script as this freezes
+    up the make process and will require the user to close the plot before make can continue.
+    As you save the plot in pickle and render it in the pdf you do not need to show it in the
+    final script.
+    """
     
 if __name__ == "__main__":
     main()

### 2025-01-24 doc/paper.qmd
paper enhance 1-3

@@
 **UK**: United Kingdom  ## 
+**US**:: United States 
 **WRDS**: Wharton Research Data Services
@@
 The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment.
-@sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper.
+@sec-task1 establishes baseline results by replicating key tables and figures from the original study using US data (1972–2006).
+@sec-task2 extends the analysis by applying the same methodology to 2007–2023 US data, enabling a comparison of how results evolve over time.
+@sec-task3 broadens the scope by applying the approach to a non-US country, requiring adjustments for different databases and market structures.
+Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper.
 The concluding remarks are provided in @sec-conclusion.
@@
 
-This paper replicates Figure 3 from the European Commission’s [-@EC_Report_2024] report, which visualizes the market shares of audit firms — Big 4, CR4, and 10KAP — by the number of PIE statutory audits conducted in 2021 across EU countries and at the EU level.
-The replication provides insights into market concentration and the dominance of major audit firms, reflecting variations in audit practices and competition across Europe.
+Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using US data (1972–2006) to establish baseline results.
+This ensures alignment with the original findings before extending the analysis in later tasks.
+By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.
 
@@
 # Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}
+
+This Section extends the analysis to 2007–2023, a period defined by major economic events such as the 2008 financial crisis and the COVID-19 pandemic, which may have influenced the informativeness of earnings announcements.
+While the task is relatively straightforward in terms of programming—requiring adjustments to the sample period—it demands careful economic interpretation of observed trends, market shifts, and potential structural changes that may influence the relationship between earnings announcements and stock returns.
+
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions2}
@@
 # Task 3 - Cross-Country Replication {#sec-task3}
+
+Task 3 extends the analysis beyond the United States by replicating Figure 1 using data from a non-U.S.
+market, providing insights into how earnings informativeness varies across different regulatory environments and market structures.
+This task requires mapping variables from CRSP/Compustat to their equivalents in Worldscope/Datastream, adjusting for differences in accounting standards, market liquidity, and institutional factors.
+While the core replication methodology remains the same, careful data handling and economic interpretation are crucial to account for cross-country differences.
+
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions3}

### 2025-01-24 doc/paper.qmd
requirements.txt libraries update

@@
   | How Much New Information Is There in Earnings?
-  | Corporate Decision-Making and Quantitative Analysis - 
-  | Individual Report\vspace{1cm}
+  | Corporate Decision-Making and Quantitative Analysis
+  | Winter 2024/25 - Individual Report\vspace{1cm}
 author:

### 2025-01-24 doc/paper.qmd
sync latest
another one

@@
 ## Results {#sec-results1}
+Comparing our replication results of Figure 1 (see Figure ## below) with those in the original report (see Figure 1 below) reveals both similarities and discrepancies.
+
+```{python}
+#| label: fig1_original_png
+#| fig-cap: "Original Figure 1 from Ball and Shivakumar (2008)"
+#| echo: false
+
+from IPython.display import Image
+
+Image(filename="fig1_original.png")
+```
+
 To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`.

### 2025-01-25 doc/paper.qmd
refine refine refine

@@
 
+-----
 The project uses data from the Audit Analytics database on Transparency Reports via Wharton Research Data Services (WRDS) for the year 2021, covering PIEs across EU countries.
@@
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
+I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:
+
+1.
+Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication.
+Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.
+
+2.
+Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement.
+According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days.
+However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window.
+Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1).
+If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day.
+Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window.
+This adjustment prevents shortening the window, ensuring a complete three-day period for capturing the full market response to earnings announcements.
+
+3.
+Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates rather than the fiscal periods they cover.
+Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days, this approach ensures consistency with the original study.
+No further adjustments are needed to realign quarters.
+
+------
 The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024.
@@
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions2}
+
+Assumptions from @sec-research_design_assumptions1 still hold
+
 ## Replication Steps {#sec-replication_steps2}
@@
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions3}
+
+It is important to use same logic in defining event windows as in Task 1 to ensure consistency https://community.developers.refinitiv.com/discussion/106705/how-to-get-only-trading-days-in-datastream-data/p1?tab=accepted
+country-specific market calendars ?
+
+We need to check whether non-US databases (Worldscope/Datastream) use the same announcement date convention or if they report earnings by fiscal period.
+
 ## Replication Steps {#sec-replication_steps3}

### 2025-01-25 doc/paper.qmd
added theoretical background on types of replication; daily stock data methodlolgy;

@@
 By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting.
+At the same time, earnings reports may play a crucial role in contracting by influencing managerial compensation, debt agreements, and other contractual mechanisms tied to financial performance [@ball_how_2008].
 The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
@@
 The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment.
-@sec-task1 establishes baseline results by replicating key tables and figures from the original study using US data (1972–2006).
-@sec-task2 extends the analysis by applying the same methodology to 2007–2023 US data, enabling a comparison of how results evolve over time.
-@sec-task3 broadens the scope by applying the approach to a non-US country, requiring adjustments for different databases and market structures.
-Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper.
+@sec-task1 follows an exact replication approach by replicating key tables and figures from the original study using US data (1972–2006) to establish baseline results.
+@sec-task2 extends the analysis through empirical generalization, applying the same methodology to 2007–2023 US data to compare how results evolve over time.
+@sec-task3 employs a generalization and extension approach by applying the methodology to a non-US country, requiring adjustments for different databases and market structures.
+This framework aligns with the replication taxonomy outlined by @salterio_replication_2022.
+Finally, @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper, following Bloomfield’s (2016) triangulation principle.
 The concluding remarks are provided in @sec-conclusion.
@@
 
-Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using US data (1972–2006) to establish baseline results.
+Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results.
 This ensures alignment with the original findings before extending the analysis in later tasks.
 By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.
+The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.
 

### 2025-01-26 doc/paper.qmd
streamline paper

@@
 The concluding remarks are provided in @sec-conclusion.
+The entire Python computation code for return calculations is available in `code/python/do_analysis.py` for detailed review if necessary.
+This paper focuses on the replication process, presenting visualizations, and discussing the results.
 
@@
 
-Task 1 is the most comprehensive, replicating key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results.
+Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results.
 This ensures alignment with the original findings before extending the analysis in later tasks.
@@
 -----
-The project uses data from the Audit Analytics database on Transparency Reports via Wharton Research Data Services (WRDS) for the year 2021, covering PIEs across EU countries.
-The replication closely follows the methodology outlined by @EC_Report_2024.
-It focuses on three key market concentration measures: the market share of the Big 4 audit firms, the CR4 market share for the largest four firms in each country, and the 10KAP market share, which includes the Big 4 and additional major networks.
-These measures provide a detailed assessment of audit firm dominance and competition, offering valuable insights into the structure and dynamics of the statutory audit market in Europe.
+##The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.
 
-The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.
-Explicit assumptions were made whenever the document by @EC_Report_2024 was unclear on how to proceed.
-The entire Python computation code for market share calculations is available in `code/python/do_analysis.py` for detailed review if necessary.
-This paper focuses on the replication process, presenting visualizations, and discussing the results.
-
-The replicated figure from original report by @EC_Report_2024 is shown below, followed by the research design choices and assumptions in @sec-research_design_assumptions, documentation of the replication steps in @sec-replication_steps, a detailed results comparison in @sec-results, and concluding remarks in @sec-conclusion.
-
-@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021.
+##@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021.
 Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report.
@@
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
-I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:
+Following @ball_how_2008, I focus the analysis on earnings announcements and stock returns from 1972 to 2006, ensuring that the data accurately reflects the original study’s methodology and findings.
+The replication aims to mirror the research design as closely as possible with the available data, maintaining consistency in sample selection, event window definitions, and return calculations.
+
+In addition, I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:
 
@@
 
+4.
+As in the original paper, firm-years are selected based on available stock return data in CRSP.
+While @ball_how_2008 restrict the sample to firms with at least 240 trading days per year, I follow the course guidance and do not apply this restriction, allowing for a slightly larger sample size.
+This adjustment should be considered when interpreting differences from the original study.
+
+By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels) from @ball_how_2008.
+A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.
+
 ------
-The aim of Assignment I is to replicate a specific empirical figure (Figure 3) from the report by @EC_Report_2024.
-This figure involves analyzing the market shares of audit firms (Big 4, CR4, and 10KAP) across EU countries and at the EU level for PIE statutory audits conducted in 2021.
-The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures.
-For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis.
-Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.
-
-The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis.
-The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].
-
-Following @EC_Report_2024, I focus the analysis on statutory audits conducted for the fiscal year 2021, ensuring that the data accurately reflects the audit market structure in the EU as specified in the original report.
-The replication aims to mirror the research design as closely as possible with the available data.
-
-In addition, I impose the following assumptions to ensure clarity and consistency where the report by @EC_Report_2024 does not provide explicit guidance:
 
@@
 
-By following the steps provided in @sec-replication_steps and adhering to the assumptions made, I successfully replicated the analysis and produced the required figure.
-A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.
+## Replication Steps {#sec-replication_steps1}
 
-## Replication Steps {#sec-replication_steps1}
+##The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures.
+For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis.
+Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.
+
+##The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis.
+The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].
 
@@
 
-Step 2: Data Preparation {#sec-step2_preparation}
+Step 2: Data Preparation
 The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021.

### 2025-01-26 doc/paper.qmd
done

@@
 This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights.
+Unlike traditional event studies that assume market efficiency, @ball_how_2008 allow for potential market mispricing by not imposing a unit slope restriction in their regressions, meaning that their approach can capture under- or overreaction to earnings announcements.
+They also emphasize that extending the event window beyond the earnings announcement period would shift the research focus from earnings “surprise” to broader financial reporting effects, such as its role in debt contracting and executive compensation.
 The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.
@@
 # Task 1 - Replication of Key Tables and Figures {#sec-task1}
-
-Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results.
-This ensures alignment with the original findings before extending the analysis in later tasks.
+Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results, ensuring alignment with the original findings before extending the analysis in @sec-task2.
 By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.
 The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.
-
------
-##The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.
-
-##@fig-market-shares illustrates the market shares of audit firms — Big 4, CR4, and 10KAP — for the number of PIE statutory audits conducted in 2021.
-Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report.
-The discussion of replication findings is presented in @sec-results.
-```{python}
-#| label: fig-market-shares
-#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
-#| fig-align: center
-#| echo: false
-
-import pickle
-import matplotlib.pyplot as plt
-
-# Load the figure from the pickle file
-with open('../output/figure3_market_shares.pickle', 'rb') as f:
-    fig = pickle.load(f)
-
-# Render the figure explicitly
-plt.figure(fig.number)
-plt.show()
-```
+The discussion of replication findings is presented in @sec-results1.
 
@@
 
+Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication.
+Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.
+
+Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates rather than the fiscal periods they cover.
+Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days, this approach ensures consistency with the original study.
+No adjustments are made to realign quarters.
+
 In addition, I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:
@@
 1.
-Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication.
-Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.
-
-2.
 Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement.
@@
 
-3.
-Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates rather than the fiscal periods they cover.
-Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days, this approach ensures consistency with the original study.
-No further adjustments are needed to realign quarters.
-
-4.
+2.
 As in the original paper, firm-years are selected based on available stock return data in CRSP.
@@
 
-By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels) from @ball_how_2008.
-A thorough step-by-step approach, with each step clearly documented, helped to understand and verify the outputs.
+3.
+
+By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated the results from @ball_how_2008.
+A thorough step-by-step approach, with each step clearly documented, helps to understand and verify the outputs.
 
@@
 Furthermore, the data vendor regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the 2022 snapshot.
-2.	The original paper outlines key terms that will be used in this project to ensure consistency and accuracy in the replication.
-@EC_Report_2024 defines the 'Big Four' as Deloitte, EY, KPMG, and PwC; the 'CR4' as the four largest audit firms in each country; and the '10KAP' as a group consisting of Baker Tilly, BDO, Deloitte, EY, Grant Thornton, KPMG, Mazars, Nexia, RSM, and PwC.
-3.	As for the geographical scope, I use the variable `trans_report_auditor_state` to identify the country associated with each audit firm rather than the audited company’s headquarter country (`headquarter_country` variable).
-Since the objective is to analyze audit market concentration and the market share of audit firms within specific countries, the country of the audit firm’s reported activity is more relevant than the headquarter country of the entities they audit.
-4.	Another potential source of discrepancies between the original and replicated tables may be the choice of variables pulled from Audit Analytics.
-For example, in the `audit_europe.feed76_transparency_reports` table, I chose `entity_map_fkey` over `entity_map_key`, as this unique identifier is created by WRDS for merging [@WRDS_Audit_Analytics_Transparency_Reports].
-Since the report does not specify the choice of variables used from the database, this could cause differences in the results.
+
 5.	For the purpose of replicating Figure 3, I use the `report_year` variable as the primary filter to define the relevant data for year 2021.
@@
 This approach simplifies the data extraction and ensures that all entries correspond to the fiscal year 2021.
+Since the report does not specify the choice of variables used from the database, this could cause differences in the results.
 
 ## Replication Steps {#sec-replication_steps1}
+The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.
 
-##The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures.
+The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures.
 For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis.
@@
 
-##The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis.
+The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis.
 The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].
 
-Step 1: Pulling the Data and Managing the Database
+**Step 1: Pulling the Data and Managing the Database**  
 This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.
@@
 
-Step 2: Data Preparation
+**Step 2: Data Preparation**  
 The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021.
@@
 
-Step 3: Analysis Implementation and Figure Reproduction
+**Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
 The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data.
@@
 ## Results {#sec-results1}
-Comparing our replication results of Figure 1 (see Figure ## below) with those in the original report (see Figure 1 below) reveals both similarities and discrepancies.
+Comparing the replication results of Figure 1 (see @fig-market-shares) with those from @ball_how_2008 (see Figure 1 below) reveals both similarities and discrepancies.
 
@@
 Image(filename="fig1_original.png")
+```
+
+@fig-market-shares illustrates the... Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report. 
+```{python}
+#| label: fig-market-shares
+#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
+#| fig-align: center
+#| echo: false
+
+import pickle
+import matplotlib.pyplot as plt
+
+# Load the figure from the pickle file
+with open('../output/figure3_market_shares.pickle', 'rb') as f:
+    fig = pickle.load(f)
+
+# Render the figure explicitly
+plt.figure(fig.number)
+plt.show()
 ```
@@
 While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.
+##we confirm?
+"The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market.
+By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system.
+The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons.
+By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking.
+Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."
 

### 2025-01-26 doc/paper.qmd
end of day

@@
 Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.
-
-Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates rather than the fiscal periods they cover.
-Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days, this approach ensures consistency with the original study.
-No adjustments are made to realign quarters.
 

### 2025-01-26 doc/paper.qmd
final for now

@@
 **HU**: Humboldt-Universität zu Berlin  
+**IDE**: Integrated Development Environment  
 **IV**: Independent Variable  
-**EU**: European Union  ##  
-**IDE**: Integrated Development Environment  
 **TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
-**UK**: United Kingdom  ##  
 **US**:: United States  

### 2025-01-26 doc/paper.qmd
save up

@@
 **TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
-**US**:: United States  
+**US**: United States  
 **WRDS**: Wharton Research Data Services

### 2025-01-27 doc/paper.qmd
semi-strong market efficiency

@@
 This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights.
+Their findings align with the semi-strong form of market efficiency, which suggests that stock prices already reflect all publicly available information, including prior signals about earnings.
 Unlike traditional event studies that assume market efficiency, @ball_how_2008 allow for potential market mispricing by not imposing a unit slope restriction in their regressions, meaning that their approach can capture under- or overreaction to earnings announcements.
@@
 
+CRSP/COMPUSTAT MERGED database allows for concurrent database access to CRSP’s stock data and Compustat’s fundamental data.
+
 The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis.
@@
 
-**Step 1: Pulling the Data and Managing the Database**  
+**Step 1: Pulling the Data and Managing the Databases**  
 This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

### 2025-01-27 doc/paper.qmd
pulling data

@@
 \setlength{\parindent}{0em}
+**BHR**: Buy-and-Hold Returns   
 **CRSP**: Center for Research in Security Prices  
@@
 3.
+Compustat includes both active and inactive firms, and the original study does not specify filtering based on firm activity.
+Thus, all firms meeting the sample selection criteria (i.e., four quarterly earnings announcements per year and available stock return data) are retained, regardless of their active status today.
+
+4.
+For historical analysis on securities, permanent identifiers, such as `PERMNO`, `PERMCO`, and `GVKEY` are used that never change for the duration of the company’s life span regardless of the name changes and are never being reused [@gow_empirical_2025].
+In this replication, variable `PERMNO` is used instead of `PERMCO` because it uniquely identifies individual securities rather than companies, ensuring that stock returns are accurately tracked at the security level.
+Since firms may have multiple share classes with distinct price movements, using `PERMNO` prevents aggregation issues that could arise with `PERMCO`, which groups all share classes under one identifier.
+
+5.
+The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually).
+Timing mismatches may arise, especially for firms with restated financials, leading to slight variations in event window alignment when calculating earnings-announcement returns.
+Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause minor differences in firm coverage or reported values.
+
+6. Since @ball_how_2008 analyze returns, I use `RET` variable in CRSP too to simplify the process. Bid and ask prices are ignored.
 
@@
 
-------
-
-1.	The original report references the reports prepared by national competent authorities (NCAs) responsible for audit oversight as the main source of data, where the data refers to the years 2020 and 2021 and was collected in 2022 [@EC_Report_2024, p.1].
-However, this replication uses data obtained from the Audit Analytics Transparency Reports database via WRDS, which provides the latest available version as of September 2024, updated quarterly [@WRDS_Audit_Analytics_Transparency_Reports].
-Due to potential adjustments and updates made to the database since the original data collection period, there may be differences that could affect the results.
-For example, audit firms may disclose updated information in subsequent reports, which would be reflected in the later database version rather than the historical snapshot used in the original report.
-Furthermore, the data vendor regularly updates its databases to correct errors and add new information, which may be included in the later data but not in the 2022 snapshot.
-
-5.	For the purpose of replicating Figure 3, I use the `report_year` variable as the primary filter to define the relevant data for year 2021.
-This choice is based on the fact that `report_year` represents the idealized fiscal year of the Transparency Report, based on the *Europe Transparency Reports Data Dictionary* by Wharton Research Data Services [-@Europe_Transparency_Reports_Data_Dictionary], which aligns directly with the year-based aggregation needed for Figure 3.
-While the `report_period_end_date` provides the exact end date of each reporting period [@Europe_Transparency_Reports_Data_Dictionary], using `report_year` allows for a consistent, annual aggregation without requiring additional alignment of various period end dates.
-This approach simplifies the data extraction and ensures that all entries correspond to the fiscal year 2021.
-Since the report does not specify the choice of variables used from the database, this could cause differences in the results.
-
 ## Replication Steps {#sec-replication_steps1}
-The analysis involves gathering and filtering Transparency Report data, identifying relevant PIEs and EU countries, and calculating the Big 4, CR4, and 10KAP market shares for each country as well as at the EU level.
-
-The replication process includes data loading, preparation, and cleaning, followed by the computation and visualization of market concentration measures.
-For Assignment I, I pulled data from the Audit Analytics database via WRDS and used the Python programming language to carry out the empirical analysis.
-Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.
-
-CRSP/COMPUSTAT MERGED database allows for concurrent database access to CRSP’s stock data and Compustat’s fundamental data.
-
-The replication is based on data pulled from the Audit Analytics Transparency Reports database, specifically from `audit_europe.feed76_transparency_reports` table, which was filtered and aggregated for the analysis.
-The table offers Transparency Reports published annually by audit firms based in the EEA and Switzerland, along with the names of all entities listed in each audit firm’s Transparency Reports [@WRDS_Audit_Analytics_Transparency_Reports].
+The analysis involves gathering and filtering stock return and earnings announcement data, linking CRSP stock data with Compustat fundamentals, and estimating the relationship between annual returns and earnings-announcement window returns.
+The replication process follows a structured workflow of data pull, preparation, and analysis, ensuring consistency with the original study.
 
 **Step 1: Pulling the Data and Managing the Databases**  
+Data is pulled from the `crsp_a_ccm.ccmxpf_lnkhist`, `crsp_a_stock.dsf`, `comp_na_daily_all.fundq` tables via WRDS, using Python for data processing and regression analysis and facilitating direct access to stock price and return data from CRSP alongside firm fundamentals from Compustat, enabling a seamless link between market and accounting data.
+Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.
+While WRDS provides extensive financial datasets, documentation on precise variable selection and dataset integration is limited, requiring additional validation and cross-referencing with prior research.
+
 This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

### 2025-01-27 code/python/pull_wrds_data.py

@@ -1,8 +1,9 @@
 # --- Header -------------------------------------------------------------------
 # See LICENSE file for details
 #
-# This code pulls data from WRDS Audit Analytics Database 
+# This code pulls data from WRDS Databases 
 # ------------------------------------------------------------------------------
+
 import os
 from getpass import getpass
 import dotenv
@@ -19,13 +20,25 @@ def main():
 
     This function reads the configuration file, gets the WRDS login credentials, and pulls the data from WRDS.
 
-    The data is then saved to a csv file.
+    The data is then saved to CSV and Parquet files.
     '''
     cfg = read_config('config/pull_data_cfg.yaml')
     wrds_login = get_wrds_login()
-    wrds_data = pull_wrds_data(cfg, wrds_login)
-    wrds_data.to_csv(cfg['audit_analytics_save_path'], index=False)
-
+    
+    # Pull CRSP and Compustat Data
+    db = wrds.Connection(
+        wrds_username=wrds_login['wrds_username'], 
+        wrds_password=wrds_login['wrds_password']
+    )
+    
+    log.info('Logged on to WRDS ...')
+    
+    pull_crsp_data(cfg, db)
+    pull_compustat_data(cfg, db)
+    pull_link_data(db)
+    
+    db.close()
+    log.info("Disconnected from WRDS")
 
 def get_wrds_login():
     '''
@@ -42,35 +55,44 @@ def get_wrds_login():
             'Please provide a WRDS password (it will not show as you type): ')
         return {'wrds_username': wrds_username, 'wrds_password': wrds_password}
 
-def pull_wrds_data(cfg, wrds_authentication):
-    '''
-    Pulls WRDS Audit Europe Transparency Report data.
-    '''
-    db = wrds.Connection(
-        wrds_username=wrds_authentication['wrds_username'], wrds_password=wrds_authentication['wrds_password']
-    )
+### LINKDATA Compustat/CRSP
+def pull_link_data(db):
+    log.info("Pulling link data Compustat/CRSP ...")
+    linkdata_df_wrds = db.get_table(library="crsp_a_ccm", table="ccmxpf_linktable")
+    linkdata_df_wrds.to_parquet("data/pulled/linkdata_compustat_crsp.parquet")
[…]

### 2025-01-28 code/python/pull_wrds_data.py
save as scv too Task 1

@@ -75,7 +75,8 @@ def pull_crsp_data(cfg, db):
     
     crsp_df_wrds = db.raw_sql(crsp_query)
     crsp_df_wrds.to_parquet(cfg['crsp_save_path'])
-    
+    crsp_df_wrds.to_csv(cfg['crsp_save_path_csv'], index=False)
+
     log.info("Pulling CRSP data ... Done!")
 
 ### COMPUSTAT DATA
@@ -91,7 +92,8 @@ def pull_compustat_data(cfg, db):
     
     fundq_df_wrds = db.raw_sql(fundq_query)
     fundq_df_wrds.to_parquet(cfg['fundq_save_path'])
-    
+    fundq_df_wrds.to_csv(cfg['fundq_save_path_csv'], index=False)
+   
     log.info("Pulling Compustat data ... Done!")
 
 if __name__ == '__main__':

### 2025-01-29 doc/paper.qmd
paper upd

@@
 **CQA**: Corporate Decision-Making and Quantitative Analysis  
+**DS**: Datastream  
 **DV**: Dependent Variable  
@@
 **WRDS**: Wharton Research Data Services  
+**WSCP**: Worldscope
 
@@
 The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
-Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to a non-U.S.
+Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to Canada as a non-U.S.
 country to explore cross-market variations.
@@
 The concluding remarks are provided in @sec-conclusion.
-The entire Python computation code for return calculations is available in `code/python/do_analysis.py` for detailed review if necessary.
+The entire Python computation code for regression run is available in `code/python/do_analysis.py` and `code/python/do_analysis-wscp.py` for detailed review if necessary.
 This paper focuses on the replication process, presenting visualizations, and discussing the results.
@@
 
+7.
+Same as @ball_how_2008, I group earnings announcements based on their actual announcement dates (`RDQ` from Compustat) rather than the fiscal periods they cover.
+Since Compustat provides the precise earnings announcement date and CRSP aligns stock returns with trading days (`date` in CRSP), this approach ensures consistency.
+So, no adjustments are made to realign quarters.
+
 By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated the results from @ball_how_2008.
@@
 ## Replication Steps {#sec-replication_steps1}
-The analysis involves gathering and filtering stock return and earnings announcement data, linking CRSP stock data with Compustat fundamentals, and estimating the relationship between annual returns and earnings-announcement window returns.
+The analysis involves gathering and filtering stock return and earnings announcement data, linking CRSP stock data with Compustat firm-level accounting data fundamentals, and estimating the relationship between annual returns and earnings-announcement window returns.
 The replication process follows a structured workflow of data pull, preparation, and analysis, ensuring consistency with the original study.
@@
 
+Since @ball_how_2008 do not explicitly describe their return computation, I compute Buy-and-Hold Returns (BHR) following the cumulative return formula as discussed in @gundersen_returns_2022.
+The BHR formula captures compounded returns over multiple days, reflecting the stock’s actual performance.
+
 The following formula is used to calculate market share:
@@
 ## Results {#sec-results1}
-Comparing the replication results of Figure 1 (see @fig-market-shares) with those from @ball_how_2008 (see Figure 1 below) reveals both similarities and discrepancies.
+Comparing the replication results of Figure 1 (see @fig-market-shares) with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
 
 ```{python}
+#| label: fig-fig1_original
+#| fig-cap: "Original Figure 1 from Ball and Shivakumar (2008)"
+#| echo: false
+
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
+
+img = mpimg.imread("fig1_original.png")
+plt.figure(figsize=(12, 20))
+plt.imshow(img)
+plt.axis("off")
+plt.show()
+
+# used in AssI Solution, I use knitr for availability of cross-referencing.
 #| label: fig1_original_png
@@
 
-from IPython.display import Image
+#from IPython.display import Image
 
-Image(filename="fig1_original.png")
+#Image(filename="fig1_original.png")
+#
 ```
@@
 @fig-market-shares illustrates the... Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report.
-```{python}
-#| label: fig-market-shares
-#| fig-cap: "Replicated Figure 3: Audit Firms' Market Shares in the EU for 2021"
-#| fig-align: center
-#| echo: false
-
-import pickle
-import matplotlib.pyplot as plt
-
-# Load the figure from the pickle file
-with open('../output/figure3_market_shares.pickle', 'rb') as f:
-    fig = pickle.load(f)
-
-# Render the figure explicitly
-plt.figure(fig.number)
-plt.show()
-```
 
@@
 While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.
-##we confirm?
+qqq we confirm?
 "The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market.
@@
 # Task 2 - Extending the Analysis to 2007–2023 {#sec-task2}
-
 This Section extends the analysis to 2007–2023, a period defined by major economic events such as the 2008 financial crisis and the COVID-19 pandemic, which may have influenced the informativeness of earnings announcements.
-While the task is relatively straightforward in terms of programming—requiring adjustments to the sample period—it demands careful economic interpretation of observed trends, market shifts, and potential structural changes that may influence the relationship between earnings announcements and stock returns.
+While the task is relatively straightforward in terms of programming—requiring adjustments to the sample period—it demands careful economic interpretation of observed trends, market shifts, and potential institutional details that may influence the relationship between earnings announcements and stock returns.
 
@@
 
-Assumptions from @sec-research_design_assumptions1 still hold
+Assumptions from @sec-research_design_assumptions1 still hold.
 
@@
 # Task 3 - Cross-Country Replication {#sec-task3}
-
-Task 3 extends the analysis beyond the United States by replicating Figure 1 using data from a non-U.S.
+Task 3 extends the analysis beyond the United States by replicating Figure 1 using 1972-2023 data (if entire data range pull possible) from a non-U.S.
 market, providing insights into how earnings informativeness varies across different regulatory environments and market structures.
 This task requires mapping variables from CRSP/Compustat to their equivalents in Worldscope/Datastream, adjusting for differences in accounting standards, market liquidity, and institutional factors.
-While the core replication methodology remains the same, careful data handling and economic interpretation are crucial to account for cross-country differences.
+Worldscope (Thomson/Refinitiv) serves as the international alternative of Compustat for earnings announcement data, while Datastream provides stock market data for non-U.S.
+companies.
+While the core replication methodology remains the same, careful data handling and economic interpretation are crucial to account for cross-country analysis with Canada.
 
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions3}
+Since this task employs a generalization and extension approach by applying the same methodology to a country different from original report, it requires adjustments for different databases and market structures.
+Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication.
+Instead, I only require stock return data and earnings announcement dates.
 
-It is important to use same logic in defining event windows as in Task 1 to ensure consistency https://community.developers.refinitiv.com/discussion/106705/how-to-get-only-trading-days-in-datastream-data/p1?tab=accepted
-country-specific market calendars ?
+Canada as the country of choice was influenced by the alignment with the methodology of @ball_how_2008, where the key factor in the selection was the availability of quarterly earnings reports, which ensures comparability with U.S.
+data.
+For Canada, the reporting frequency is majority 4x, with some 2x, similar to the US [@short_short_2025].
+While Canada has a smaller market size than the U.S., its regulatory environment, reporting frequency, and institutional settings are highly comparable, making it an optimal choice for the non-U.S.
+analysis.
+Additionally, Canada features a developed capital market with high trading volume and liquidity, ensuring that stock price reactions to earnings announcements are observable in the replication.
+A further advantage is that Canadian firms registered with the U.S.
+Securities and Exchange Commission (SEC) can report under U.S.
+GAAP, making their financial disclosures fully compatible with U.S.
+firms.
+This reduces methodological differences to the original study.
 
-We need to check whether non-US databases (Worldscope/Datastream) use the same announcement date convention or if they report earnings by fiscal period.
+In addition, I impose the following assumptions apart from those listed in @sec-research_design_assumptions1 to ensure generalization and extension approach due to usage of other databases or where @ball_how_2008 do not provide explicit guidance:
+
+1.
+To ensure a smooth and conflict-free process, I handle the WSCP/Datastream workflow separately, preventing potential interference with the CRSP/Compustat pull process and improving debugging efficiency.
+Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets is chosen for modular approach.
+Therefore, I isolate the data pull for @sec-task3 into `pull_wrds_data-wscp`, thus reducing complicated dependencies across tasks.
+To maintain structural consistency, I implement same approach for subsequent steps, including data preparation and analysis.
+
+2.
+Since I do not perform subgroup analysis for December and non-December fiscal year end firms as in Table 2 Panels C-D, `item5350` for FISCAL PERIOD END DATE is not relevant for this task, as Figure 1 applies to the analysis of the entire dataset.
+So, the sample is all firm-years with available data on the quarterly Worlscope and daily Datastream files.
+
+3.
+I verified whether Worldscope and Datastream follow the same earnings announcement date convention as Compustat or if they report earnings based on fiscal periods.
+I decided to use Worldscope items 5901–5904 from historical stock-related data in `wrds_ws_stock`, which represent the actual date when a company publicly reports its earnings for each quarter, where, however, data for these fields is generally not available prior to 1992.
+[@thomson_financial_worldscope_2007, p.281].
+This may cause limited data sample size.
+
+4.
+This task is a generalization to a non-U.S.
+setting, meaning methodological differences will certainly arise due to variations in data structure and reporting standards.
+Worldscope - Stock Data `wrds_ws_stock` table is updated quarterly, while Datastream Daily Stock File `wrds_ds2dsf` is updated weekly, which may introduce timing mismatches when aligning financial fundamentals with stock returns.
+Given that, future applications should consider database updates and coverage differences between CRSP and Datastream.
+
+5. Similar to @sec-task1, I use returns `ret` variable in Datastream to simplify the process, presented as percentage change. Bid and ask prices are ignored.
+
+6. I ignore the currency effect (CAD or USD) in DS table, as returns are measured in percentages, making them relative rather than absolute values.
 
 ## Replication Steps {#sec-replication_steps3}
+Same as in @sec-task1 the analysis involves gathering and filtering stock return and earnings announcement data, linking Datastream stock data with WSCP (Worldscope), and estimating the relationship between annual returns and earnings-announcement window returns.
+The replication process follows a structured workflow of data pull, preparation, and analysis, ensuring consistency with the original study.
+
+**Step 1: Pulling the Data and Managing the Databases**  
+I follow the linking approach between Worldscope and Datastream based on @dai_research_2021.
+The original study uses data from 1972 onward, while Worldscope's `year_` variable only provides data starting from 1980 [@wharton_research_data_services_worldscope_2025].
+This constraint may lead to differences in sample coverage.
+Hence, filter Datastream `marketdate` to 1980 to prevent mismatched observations where stock data exists but earnings do not.
+
+The data pull step retrieves quarterly earnings announcement dates from Worldscope and daily stock returns from Datastream, filtering for Canadian firms from 1980 onward.
+The datasets are saved separately and later merged using firm-level identifiers.
+Only common equity (`typecode` = EQ) is included to ensure consistency with CRSP.
+
+**Step 2: Data Preparation**  
+If a firm has missing values for any of the Earnings Per Share Report Date fields (`item5901`–`item5904`), it does not meet the criteria set by @ball_how_2008 and was excluded from the sample.
+
+**Step 3: Analysis Implementation and Reproduction of Tables and Figure**
+
 ## Results {#sec-results3}
+Comparing the replication results with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
+
+qqq Comparing the replication results from Task 1&2 (see @ and @) with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
 
@@
 The study contributes to the ongoing discussion on market efficiency and the economic role of corporate disclosures by providing empirical evidence on how earnings informativeness has evolved over time and across jurisdictions.
-The cross-country analysis highlights variations in market responses to earnings announcements, suggesting that institutional factors, market structures, and investor behavior play a role in shaping how financial information is processed.
+The cross-country analysis with Canada highlights variations in market responses to earnings announcements, suggesting that institutional factors, market structures, and investor behavior play a role in shaping how financial information is processed.
 These findings have implications for investors, analysts, and policymakers, as they underscore the importance of regulatory consistency and market transparency in shaping the effectiveness of financial reporting.

### 2025-01-29 code/python/do_analysis-wscp.py
do analysis wscp

@@ -1,0 +1,1 @@
+## TAKE A LOOK AT SS24

### 2025-01-29 code/python/pull_wrds_data-wscp.py
commit

@@ -1,12 +1,11 @@
 # --- Header -------------------------------------------------------------------
 # See LICENSE file for details
 #
-# This code pulls data from WRDS Worldscope Database
+# This code pulls data from WRDS Worldscope and Datastream Databases
 # ------------------------------------------------------------------------------
 import os
 from getpass import getpass
 import dotenv
-
 import pandas as pd
 from utils import read_config, setup_logging
 import wrds
@@ -14,85 +13,107 @@ import wrds
 log = setup_logging()
 
 def main():
-    '''
+    """
     Main function to pull data from WRDS.
 
-    This function reads the configuration file, gets the WRDS login credentials, and pulls the data from WRDS.
+    This function reads the configuration file, gets the WRDS login credentials, 
+    and pulls the data from WRDS.
 
-    The data is then saved to a csv file.
-    '''
+    The data is then saved to CSV and Parquet files.
+    """
     cfg = read_config('config/pull_data_cfg.yaml')
     wrds_login = get_wrds_login()
-    wrds_data = pull_wrds_data(cfg, wrds_login)
-    wrds_data.to_csv(cfg['worldscope_sample_save_path'], index=False)
+    
+    # Pull data from WRDS
+    worldscope_df, ds_df, linkdata_df = pull_wrds_data(cfg, wrds_login)
+
+    # Save pulled data
+    worldscope_df.to_csv(cfg['worldscope_sample_save_path_csv'], index=False)
+    worldscope_df.to_parquet(cfg['worldscope_sample_save_path'], index=False)
+
+    ds_df.to_csv(cfg['datastream_sample_save_path_csv'], index=False)
+    ds_df.to_parquet(cfg['datastream_sample_save_path'], index=False)
+
+    linkdata_df.to_csv(cfg['link_ds_ws_save_path_csv'], index=False)
+    linkdata_df.to_parquet(cfg['link_ds_ws_save_path'], index=False)
 
 
 def get_wrds_login():
-    '''
+    """
     Gets the WRDS login credentials.
-    '''
+    """
     if os.path.exists('secrets.env'):
         dotenv.load_dotenv('secrets.env')
         wrds_username = os.getenv('WRDS_USERNAME')
         wrds_password = os.getenv('WRDS_PASSWORD')
-        return {'wrds_username': wrds_username, 'wrds_password': wrds_password}
     else:
[…]

### 2025-01-29 code/python/pull_wrds_data-wscp.py
pull

@@ -65,37 +65,38 @@ def pull_wrds_data(cfg, wrds_authentication):
     log.info("Logged on to WRDS ...")
 
 
-    ## WORLDCSOPE DATA
-    log.info("Pulling Worldscope data ... ")
-    # Prepare wrds_ws_stock_vars and wrds_ws_stock_filter
-    if cfg.get( 'worldscope_vars'):
-        worldscope_vars = ', ' .join(cfg['worldscope_vars'])
-    else:
-        worldscope_vars = '*'
-    if cfg.get('worldscope_filter'):
-        worldscope_filter = ' AND ' .join(cfg['worldscope_filter'])
-    else:
-        worldscope_filter = '1=1'
 
-    worldscope_query = f"SELECT {worldscope_vars} FROM tr_worldscope.wrds_ws_stock WHERE {worldscope_filter}"
+    log.info("Pulling Worldscope data ... ") # Pull Worldscope Stock Data
+    # Prepare the variables and filters for the WRDS Worldscope stock data query
+    if cfg.get('wrds_ws_stock_vars'):
+        wrds_ws_stock_vars = ', '.join(cfg['wrds_ws_stock_vars'])
+    else:
+        wrds_ws_stock_vars = '*'
+    
+    if cfg.get('wrds_ws_stock_filter'):
+        wrds_ws_stock_filter = ' AND '.join(cfg['wrds_ws_stock_filter'])
+    else:
+        wrds_ws_stock_filter = '1=1' # To ensure the query is valid and can run even if no filters are specified.
+
+    worldscope_query = f"SELECT {wrds_ws_stock_vars} FROM tr_worldscope.wrds_ws_stock WHERE {wrds_ws_stock_filter}"
     log.info(f"Executing query: {worldscope_query}")
-    worldscope_df_wrds = db.raw_sql(worldscope_query)
+    worldscope_df = db.raw_sql(worldscope_query)
 
     log.info("Pulling Worldscope data ... Done!")
 
 
-    ## DATASTREAM DATA
-    log.info("Pulling Datastream data ... ")
 
-    # Prepare ds_vars and ds_filter
+    log.info("Pulling Datastream data ... ") # Pull Datastream Daily Data
+    # Prepare the variables and filters
     if cfg.get('ds_vars'):
-        worldscope_vars = ', ' .join(cfg['ds_vars'])
+        ds_vars = ', '.join(cfg['ds_vars'])
     else:
-        worldscope_vars = '*'
[…]

### 2025-01-29 doc/paper.qmd
prep

@@
 
+The pull step results into three comprehensive datasets: DS table with 27,950,012, Link table with 77,944, WSCP table with 1,942,202 observations.
+
 **Step 2: Data Preparation**
+
 If a firm has missing values for any of the Earnings Per Share Report Date fields (`item5901`–`item5904`), it does not meet the criteria set by @ball_how_2008 and was excluded from the sample.

### 2025-01-29 code/python/prepare_data-wscp.py

@@ -1,0 +1,84 @@
+# --- Header -------------------------------------------------------------------
+# Prepare the pulled data for further analysis as per Task 3 requirements
+#
+# (C) Melisa Mazaeva - See LICENSE file for details
+# ------------------------------------------------------------------------------
+
+import pandas as pd
+from utils import read_config, setup_logging
+
+log = setup_logging()
+
+def main():
+    log.info("Preparing data for analysis ...")
+    cfg = read_config('config/prepare_data_cfg.yaml')
+
+    # Load the pulled datasets
+    ws_stock = pd.read_csv(cfg['worldscope_sample_save_path_csv'])
+    link_ds_ws = pd.read_csv(cfg['link_ds_ws_save_path_csv'])
+    ds2dsf = pd.read_csv(cfg['datastream_sample_save_path_csv'])
+    
+
+    # Step 1: Merge Worldscope with the Linking Table
+    log.info("Merging Worldscope with Linking Table...")
+    ws_link_merged = merge_worldscope_link(ws_stock, link_ds_ws)
+
+    # Step 2: Merge the previous with Datastream data
+    log.info("Merging merged data with Datastream...")
+    final_merged = merge_with_datastream(ws_link_merged, ds2dsf)
+
+    # Step 3: Adjust earnings announcement dates to match trading days
+    #log.info("Adjusting earnings announcement dates...")
+    #final_merged = adjust_announcement_dates(final_merged)
+
+    # Save the prepared dataset
+    final_merged.to_csv(cfg['prepared_data_save_path'], index=False)
+    final_merged.to_parquet(cfg['prepared_data_save_path_parquet'], index=False)
+
+    log.info(f"Prepared data saved to {cfg['prepared_data_save_path']} (CSV)")
+    log.info(f"Prepared data saved to {cfg['prepared_data_save_path_parquet']} (Parquet)")
+
+    log.info("Preparing data for analysis ... Done!")
+
+
+def merge_worldscope_link(ws_stock, link_ds_ws):
+    """
+    Merge Worldscope stock data with the linking table.
+    Uses `code` (QA ID for Worldscope) to join with the linking table.
+    """
+    ws_link_merged = ws_stock.merge(link_ds_ws, left_on="code", right_on="code", how="inner")
+    log.info(f"Merged Worldscope and Linking Table. Observations: {len(ws_link_merged)}")
+    return ws_link_merged
+
+
+def merge_with_datastream(ws_link_merged, ds2dsf):
+    """
[…]

### 2025-01-29 code/python/prepare_data-wscp.py
prep 2

@@ -32,11 +32,11 @@ def main():
     #final_merged = adjust_announcement_dates(final_merged)
 
     # Save the prepared dataset
-    final_merged.to_csv(cfg['prepared_data_save_path'], index=False)
-    final_merged.to_parquet(cfg['prepared_data_save_path_parquet'], index=False)
+    final_merged.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    final_merged.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
-    log.info(f"Prepared data saved to {cfg['prepared_data_save_path']} (CSV)")
-    log.info(f"Prepared data saved to {cfg['prepared_data_save_path_parquet']} (Parquet)")
+    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV)")
+    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
 
     log.info("Preparing data for analysis ... Done!")
 

### 2025-01-29 doc/paper.qmd
prep

@@
 To ensure a smooth and conflict-free process, I handle the WSCP/Datastream workflow separately, preventing potential interference with the CRSP/Compustat pull process and improving debugging efficiency.
-Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets is chosen for modular approach.
-Therefore, I isolate the data pull for @sec-task3 into `pull_wrds_data-wscp`, thus reducing complicated dependencies across tasks.
-To maintain structural consistency, I implement same approach for subsequent steps, including data preparation and analysis.
+Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets demands modular approach.
+Therefore, I isolate the workflow for @sec-task3 into working files `...-wscp`, thus reducing complicated dependencies across tasks.
 
@@
 **Step 2: Data Preparation**  
+First, I merged Worldscope stock data with the linking table using `code` as unique identifier, resulting in 747,760 observations.
+This merged dataset was then joined with Datastream daily stock data using `infocode`, producing a final dataset with 10,249,737 observations.
 

### 2025-01-29 code/python/prepare_data-wscp.py

@@ -27,10 +27,6 @@ def main():
     log.info("Merging merged data with Datastream...")
     final_merged = merge_with_datastream(ws_link_merged, ds2dsf)
 
-    # Step 3: Adjust earnings announcement dates to match trading days
-    #log.info("Adjusting earnings announcement dates...")
-    #final_merged = adjust_announcement_dates(final_merged)
-
     # Save the prepared dataset
     final_merged.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
     final_merged.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
@@ -60,25 +56,7 @@ def merge_with_datastream(ws_link_merged, ds2dsf):
     log.info(f"Merged with Datastream. Final observations: {len(final_merged)}")
     return final_merged
 
-'''
-def adjust_announcement_dates(df):
-    """
-    Ensure that earnings announcement dates align with actual trading days.
-    If a date falls on a non-trading day, shift to the next available trading day.
-    """
-    def shift_to_trading_day(announcement_date, trading_dates):
-        return min([d for d in trading_dates if d >= announcement_date], default=None)
 
-    df["marketdate"] = pd.to_datetime(df["marketdate"])
-    trading_days = set(df["marketdate"])
-
-    for col in ["item5901", "item5902", "item5903", "item5904"]:
-        df[col] = pd.to_datetime(df[col])
-        df[col] = df[col].apply(lambda x: shift_to_trading_day(x, trading_days))
-
-    log.info("Earnings announcement dates adjusted.")
-    return df
-'''
 
 if __name__ == "__main__":
     main()

### 2025-01-29 code/python/pull_wrds_data-wscp.py

@@ -1,7 +1,7 @@
 # --- Header -------------------------------------------------------------------
 # See LICENSE file for details
 #
-# This code pulls data from WRDS Worldscope and Datastream Databases
+# This code pulls data from WRDS Worldscope and Datastream Databases and links them
 # ------------------------------------------------------------------------------
 import os
 from getpass import getpass
@@ -65,8 +65,7 @@ def pull_wrds_data(cfg, wrds_authentication):
     log.info("Logged on to WRDS ...")
 
 
-
-    log.info("Pulling Worldscope data ... ") # Pull Worldscope Stock Data
+    log.info("Pulling Worldscope data ... ")
     # Prepare the variables and filters for the WRDS Worldscope stock data query
     if cfg.get('wrds_ws_stock_vars'):
         wrds_ws_stock_vars = ', '.join(cfg['wrds_ws_stock_vars'])
@@ -82,12 +81,12 @@ def pull_wrds_data(cfg, wrds_authentication):
     log.info(f"Executing query: {worldscope_query}")
     worldscope_df = db.raw_sql(worldscope_query)
 
-    log.info("Pulling Worldscope data ... Done!")
+    log.info("Pulling WSCP data ... Done!")
 
 
 
-    log.info("Pulling Datastream data ... ") # Pull Datastream Daily Data
-    # Prepare the variables and filters
+    log.info("Pulling DS data ... ")
+    # Prepare the variables and filters likewise to pull from Datastream Daily Data
     if cfg.get('ds_vars'):
         ds_vars = ', '.join(cfg['ds_vars'])
     else:
@@ -101,13 +100,12 @@ def pull_wrds_data(cfg, wrds_authentication):
     ds_query = f"SELECT {ds_vars} FROM tr_ds_equities.wrds_ds2dsf WHERE {ds_filter}"
     log.info(f"Executing query: {ds_query}")
     ds_df = db.raw_sql(ds_query)
+    log.info("Pulling DS data ... Done!")
 
-    log.info("Pulling Datastream data ... Done!")
 
-
-    log.info("Pulling link data Worldscope/Datastream... ") 
+    log.info("Pulling link data WSCP/DS... ") 
     linkdata_df = db.get_table(library="wrdsapps_link_datastream_wscope", table="ds2ws_linktable") # Pull link Data
-    log.info("Pulling link data Worldscope/Datastream... Done!")
+    log.info("Pulling link data WSCP/DS... Done!")
 
     db.close()
     log.info("Disconnected from WRDS")

### 2025-01-29 code/python/prepare_data-wscp.py
prep 3

@@ -18,7 +18,6 @@ def main():
     link_ds_ws = pd.read_csv(cfg['link_ds_ws_save_path_csv'])
     ds2dsf = pd.read_csv(cfg['datastream_sample_save_path_csv'])
     
-
     # Step 1: Merge Worldscope with the Linking Table
     log.info("Merging Worldscope with Linking Table...")
     ws_link_merged = merge_worldscope_link(ws_stock, link_ds_ws)
@@ -27,9 +26,13 @@ def main():
     log.info("Merging merged data with Datastream...")
     final_merged = merge_with_datastream(ws_link_merged, ds2dsf)
 
+    # Step 3: Filter for valid earnings announcement dates
+    log.info("Filtering firm-year observations based on earnings announcement criteria...")
+    final_filtered = filter_valid_earnings(final_merged)
+
     # Save the prepared dataset
-    final_merged.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    final_merged.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+    final_filtered.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    final_filtered.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
     log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV)")
     log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
@@ -56,6 +59,40 @@ def merge_with_datastream(ws_link_merged, ds2dsf):
     log.info(f"Merged with Datastream. Final observations: {len(final_merged)}")
     return final_merged
 
+
+def filter_valid_earnings(df):
+    """
+    Filters out firm-year observations where:
+    1. Any of the earnings announcement dates (items 5901-5904) are missing.
+    2. All four earnings announcements must fall within the same calendar year.
+    """
+    initial_count = len(df)
+
+    # Drop rows where any of the quarterly earnings announcement dates are missing
+    df_filtered = df.dropna(subset=['item5901', 'item5902', 'item5903', 'item5904'])
+    after_na_drop = len(df_filtered)
+    log.info(f"Dropped {initial_count - after_na_drop} rows due to missing earnings announcement dates.")
+
+    # Ensure all four announcements fall within the same calendar year
[…]

### 2025-01-29 doc/paper.qmd
prep filter

@@
 
-If a firm has missing values for any of the Earnings Per Share Report Date fields (`item5901`–`item5904`), it does not meet the criteria set by @ball_how_2008 and was excluded from the sample.
+If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample.
+This filtering step removed 3,609,492 firm-year observations.
+Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year.
+The final dataset consists of only 643,452 valid firm-year observations, starting in 1996 only, signaling the potential difference in the acocunting standards between the U.S.
+and Canada.
 

### 2025-01-29 code/python/prepare_data-wscp.py

@@ -69,16 +69,25 @@ def filter_valid_earnings(df):
     initial_count = len(df)
 
     # Drop rows where any of the quarterly earnings announcement dates are missing
-    df_filtered = df.dropna(subset=['item5901', 'item5902', 'item5903', 'item5904'])
+    df_filtered = df.dropna(subset=['item5901', 'item5902', 'item5903', 'item5904']).copy()
     after_na_drop = len(df_filtered)
     log.info(f"Dropped {initial_count - after_na_drop} rows due to missing earnings announcement dates.")
 
-    # Ensure all four announcements fall within the same calendar year
-    df_filtered['year_5901'] = pd.to_datetime(df_filtered['item5901']).dt.year
-    df_filtered['year_5902'] = pd.to_datetime(df_filtered['item5902']).dt.year
-    df_filtered['year_5903'] = pd.to_datetime(df_filtered['item5903']).dt.year
-    df_filtered['year_5904'] = pd.to_datetime(df_filtered['item5904']).dt.year
+    # Convert date columns to string first (prevents issues with mixed types)
+    date_columns = ['item5901', 'item5902', 'item5903', 'item5904']
+    df_filtered[date_columns] = df_filtered[date_columns].astype(str)
 
+    # Convert date columns to datetime (with error handling)
+    for col in date_columns:
+        df_filtered[col] = pd.to_datetime(df_filtered[col], format="%m/%d/%y", errors='coerce')
+
+    # Extract year from each earnings announcement
+    df_filtered['year_5901'] = df_filtered['item5901'].dt.year
+    df_filtered['year_5902'] = df_filtered['item5902'].dt.year
+    df_filtered['year_5903'] = df_filtered['item5903'].dt.year
+    df_filtered['year_5904'] = df_filtered['item5904'].dt.year
+
+    # Ensure all four announcements fall within the same calendar year
     df_filtered = df_filtered[
         (df_filtered['year_5901'] == df_filtered['year_5902']) &
         (df_filtered['year_5901'] == df_filtered['year_5903']) &

### 2025-01-29 doc/paper.qmd
prep upd

@@
 
+7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure the inclusion of trading days around earnings announcements.
+
 ## Replication Steps {#sec-replication_steps3}
@@
 If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample.
-This filtering step removed 3,609,492 firm-year observations.
+This filtering step removed 3,609,492 missing firm-year observations.
 Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year.
-The final dataset consists of only 643,452 valid firm-year observations, starting in 1996 only, signaling the potential difference in the acocunting standards between the U.S.
+The final dataset consists of only 616,980 valid firm-year observations, starting in 1996 only, signaling the potential difference in the accounting standards between the U.S.
 and Canada.

### 2025-01-29 code/python/prepare_data-wscp.py

@@ -65,6 +65,7 @@ def filter_valid_earnings(df):
     Filters out firm-year observations where:
     1. Any of the earnings announcement dates (items 5901-5904) are missing.
     2. All four earnings announcements must fall within the same calendar year.
+    3. All four earnings announcement dates must be in the year **≤2023**.
     """
     initial_count = len(df)
 
@@ -73,11 +74,8 @@ def filter_valid_earnings(df):
     after_na_drop = len(df_filtered)
     log.info(f"Dropped {initial_count - after_na_drop} rows due to missing earnings announcement dates.")
 
-    # Convert date columns to string first (prevents issues with mixed types)
+    # Convert date columns to datetime format
     date_columns = ['item5901', 'item5902', 'item5903', 'item5904']
-    df_filtered[date_columns] = df_filtered[date_columns].astype(str)
-
-    # Convert date columns to datetime (with error handling)
     for col in date_columns:
         df_filtered[col] = pd.to_datetime(df_filtered[col], format="%m/%d/%y", errors='coerce')
 
@@ -95,6 +93,16 @@ def filter_valid_earnings(df):
     ]
     after_year_check = len(df_filtered)
     log.info(f"Dropped {after_na_drop - after_year_check} rows due to earnings announcements spanning multiple years.")
+
+    # Remove firm-year observations where any date is beyond 2023
+    df_filtered = df_filtered[
+        (df_filtered['year_5901'] <= 2023) &
+        (df_filtered['year_5902'] <= 2023) &
+        (df_filtered['year_5903'] <= 2023) &
+        (df_filtered['year_5904'] <= 2023)
+    ]
+    after_2023_check = len(df_filtered)
+    log.info(f"Dropped {after_year_check - after_2023_check} rows due to earnings announcements beyond 2023.")
 
     # Drop the temporary year columns
     df_filtered = df_filtered.drop(columns=['year_5901', 'year_5902', 'year_5903', 'year_5904'])

### 2025-01-29 code/python/prepare_data-wscp.py
pr

@@ -104,12 +104,20 @@ def filter_valid_earnings(df):
     after_2023_check = len(df_filtered)
     log.info(f"Dropped {after_year_check - after_2023_check} rows due to earnings announcements beyond 2023.")
 
+    # Count NaN values in the 'ret' column before replacing them
+    nan_count = df_filtered['ret'].isna().sum()
+    # Replace NaN values in the 'ret' column with 0
+    df_filtered['ret'] = df_filtered['ret'].fillna(0)
+    log.info(f"Replaced {nan_count} NaN values in 'ret' column with 0.")
+
     # Drop the temporary year columns
     df_filtered = df_filtered.drop(columns=['year_5901', 'year_5902', 'year_5903', 'year_5904'])
 
     log.info(f"Final dataset size after filtering: {len(df_filtered)}")
 
     return df_filtered
+
+
 
 
 if __name__ == "__main__":

### 2025-01-30 code/python/prepare_data-wscp.py
prep new

@@ -110,12 +110,17 @@ def filter_valid_earnings(df):
     df_filtered['ret'] = df_filtered['ret'].fillna(0)
     log.info(f"Replaced {nan_count} NaN values in 'ret' column with 0.")
 
+    # Count rows where ret=0
+    zero_ret_count = (df_filtered['ret'] == 0).sum()
+    log.info(f"Number of rows where 'ret' = 0: {zero_ret_count}")
+
     # Drop the temporary year columns
     df_filtered = df_filtered.drop(columns=['year_5901', 'year_5902', 'year_5903', 'year_5904'])
 
     log.info(f"Final dataset size after filtering: {len(df_filtered)}")
 
     return df_filtered
+
 
 
 

### 2025-01-30 doc/paper.qmd
prep

@@
 First, I merged Worldscope stock data with the linking table using `code` as unique identifier, resulting in 747,760 observations.
-This merged dataset was then joined with Datastream daily stock data using `infocode`, producing a final dataset with 10,249,737 observations.
+This merged dataset was then joined with Datastream daily stock data using unique `infocode`, producing a final dataset with 10,249,737 observations.
 
@@
 Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year.
-The final dataset consists of only 616,980 valid firm-year observations, starting in 1996 only, signaling the potential difference in the accounting standards between the U.S.
+The final dataset consists of only 616,980 valid firm-year observations, starting in 1996 only, signaling the potential difference in the accounting reporting standards between the U.S.
 and Canada.

### 2025-01-30 code/python/prepare_data-wscp.py

@@ -66,6 +66,7 @@ def filter_valid_earnings(df):
     1. Any of the earnings announcement dates (items 5901-5904) are missing.
     2. All four earnings announcements must fall within the same calendar year.
     3. All four earnings announcement dates must be in the year **≤2023**.
+    Also, identifies the years in `marketdate` where `ret = 0` is most frequent.
     """
     initial_count = len(df)
 
@@ -110,9 +111,21 @@ def filter_valid_earnings(df):
     df_filtered['ret'] = df_filtered['ret'].fillna(0)
     log.info(f"Replaced {nan_count} NaN values in 'ret' column with 0.")
 
+    # Convert 'marketdate' to datetime format
+    df_filtered['marketdate'] = pd.to_datetime(df_filtered['marketdate'], errors='coerce')
+
+    # Extract year from 'marketdate'
+    df_filtered['market_year'] = df_filtered['marketdate'].dt.year
+
     # Count rows where ret=0
     zero_ret_count = (df_filtered['ret'] == 0).sum()
     log.info(f"Number of rows where 'ret' = 0: {zero_ret_count}")
+
+    # Identify years with the most occurrences of ret = 0
+    zero_ret_by_year = df_filtered[df_filtered['ret'] == 0]['market_year'].value_counts()
+    
+    log.info("Top 5 years with the most occurrences of 'ret = 0':")
+    log.info(zero_ret_by_year.head(5).to_string())
 
     # Drop the temporary year columns
     df_filtered = df_filtered.drop(columns=['year_5901', 'year_5902', 'year_5903', 'year_5904'])

### 2025-01-30 doc/paper.qmd
prep

@@
 
-7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure the inclusion of trading days around earnings announcements.
+7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure higher inclusion of trading days around earnings announcements.
 

### 2025-01-30 code/python/prepare_data-wscp.py

@@ -66,6 +66,7 @@ def filter_valid_earnings(df):
     1. Any of the earnings announcement dates (items 5901-5904) are missing.
     2. All four earnings announcements must fall within the same calendar year.
     3. All four earnings announcement dates must be in the year **≤2023**.
+    4. Removes rows where all four earnings announcement dates are identical.
     Also, identifies the years in `marketdate` where `ret = 0` is most frequent.
     """
     initial_count = len(df)
@@ -104,6 +105,16 @@ def filter_valid_earnings(df):
     ]
     after_2023_check = len(df_filtered)
     log.info(f"Dropped {after_year_check - after_2023_check} rows due to earnings announcements beyond 2023.")
+
+    # Remove rows where all four announcement dates are identical
+    before_unique_filter = len(df_filtered)
+    df_filtered = df_filtered[
+        ~((df_filtered['item5901'] == df_filtered['item5902']) &
+          (df_filtered['item5901'] == df_filtered['item5903']) &
+          (df_filtered['item5901'] == df_filtered['item5904']))
+    ]
+    after_unique_filter = len(df_filtered)
+    log.info(f"Dropped {before_unique_filter - after_unique_filter} rows where all four earnings announcements were identical.")
 
     # Count NaN values in the 'ret' column before replacing them
     nan_count = df_filtered['ret'].isna().sum()

### 2025-01-30 code/python/prepare_data-wscp.py
prep return days

@@ -17,7 +17,7 @@ def main():
     ws_stock = pd.read_csv(cfg['worldscope_sample_save_path_csv'])
     link_ds_ws = pd.read_csv(cfg['link_ds_ws_save_path_csv'])
     ds2dsf = pd.read_csv(cfg['datastream_sample_save_path_csv'])
-    
+
     # Step 1: Merge Worldscope with the Linking Table
     log.info("Merging Worldscope with Linking Table...")
     ws_link_merged = merge_worldscope_link(ws_stock, link_ds_ws)
@@ -30,9 +30,15 @@ def main():
     log.info("Filtering firm-year observations based on earnings announcement criteria...")
     final_filtered = filter_valid_earnings(final_merged)
 
+    # Step 4: Match earnings announcements with stock returns
+    final_matched = match_earnings_to_market_dates(final_filtered)
+
+    # Step 5: Compute deviation statistics
+    deviation_stats = compute_deviation_statistics(final_matched)
+
     # Save the prepared dataset
-    final_filtered.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    final_filtered.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+    final_matched.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    final_matched.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
     log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV)")
     log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
@@ -146,7 +152,76 @@ def filter_valid_earnings(df):
     return df_filtered
 
 
+def match_earnings_to_market_dates(df):
+    """
+    Match quarterly earnings announcement dates (item5901-4) to market trading dates per firm.
+    Assign the closest available stock return (ret) for each earnings date.
+    """
 
+    log.info("Matching earnings announcements to valid trading days...")
+
+    # Convert 'marketdate' to datetime
+    df["marketdate"] = pd.to_datetime(df["marketdate"], errors="coerce")
+
+    # Filter only necessary columns for efficiency
+    market_data = df[["infocode", "marketdate", "ret"]].drop_duplicates()
+
+    # Create a lookup dictionary {infocode: DataFrame with marketdate & ret}
+    market_lookup = {
[…]

### 2025-01-30 code/python/prepare_data-wscp-copy.py
process

@@ -22,13 +22,26 @@ def main():
     log.info("Merging Worldscope with Linking Table...")
     ws_link_merged = merge_worldscope_link(ws_stock, link_ds_ws)
 
+    # Step 2: Merge the previous with Datastream data
+    log.info("Merging merged data with Datastream...")
+    final_merged = merge_with_datastream(ws_link_merged, ds2dsf)
 
+    # Step 3: Filter for valid earnings announcement dates
+    log.info("Filtering firm-year observations based on earnings announcement criteria...")
+    final_filtered = filter_valid_earnings(final_merged)
+
+    # Step 4: Match earnings announcements with stock returns
+    final_matched = match_earnings_to_market_dates(final_filtered)
+
+    # Step 5: Compute deviation statistics
+    deviation_stats = compute_deviation_statistics(final_matched)
 
     # Save the prepared dataset
-    ws_link_merged.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    ws_link_merged.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+    final_matched.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    final_matched.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
-    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
+    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV)")
+    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
 
     log.info("Preparing data for analysis ... Done!")
 
@@ -37,48 +50,12 @@ def merge_worldscope_link(ws_stock, link_ds_ws):
     """
     Merge Worldscope stock data with the linking table.
     Uses `code` (QA ID for Worldscope) to join with the linking table.
-    Keeps only the relevant columns: year_, item6105, item5901, item5902, item5903, item5904, infocode.
     """
-    # Merge datasets
     ws_link_merged = ws_stock.merge(link_ds_ws, left_on="code", right_on="code", how="inner")
     log.info(f"Merged Worldscope and Linking Table. Observations: {len(ws_link_merged)}")
-
-    # Keep only relevant columns
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
expand

@@ -22,13 +22,15 @@ def main():
     log.info("Merging Worldscope with Linking Table...")
     ws_link_merged = merge_worldscope_link(ws_stock, link_ds_ws)
 
+    # Step 2: Pivot dataset to long format
+    log.info("Pivoting merged dataset to long format...")
+    ws_long = pivot_longer_earnings(ws_link_merged)
 
+    # Save the pivoted dataset directly to the predefined paths
+    ws_long.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    ws_long.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
-    # Save the prepared dataset
-    ws_link_merged.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    ws_link_merged.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
-
-    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
+    log.info(f"Pivoted data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
 
     log.info("Preparing data for analysis ... Done!")
 
@@ -61,7 +63,7 @@ def pivot_longer_earnings(ws_link_merged):
         id_vars=["year_", "item6105", "infocode"],  # Keep these as identifiers
         value_vars=["item5901", "item5902", "item5903", "item5904"],  # Pivot these columns
         var_name="quarter", 
-        value_name="announcement_date"
+        value_name="rdq"
     )
 
     # Map quarter names for clarity
@@ -77,6 +79,33 @@ def pivot_longer_earnings(ws_link_merged):
     log.info(f"Pivoted dataset. New number of rows: {len(ws_long)}")
 
     return ws_long
+
+def expand_event_window(ws_long):
+    """
+    Expands the dataset by applying a ±1 day offset to each earnings announcement date.
+    Creates additional rows for Day -1, Day 0, and Day +1.
+    """
+    log.info("Expanding dataset to include event windows (-1, 0, +1 days)...")
+
+    # Define offsets: -1 (before), 0 (announcement day), +1 (after)
+    offsets = [-1, 0, 1]
+
+    # Create a list of expanded rows by iterating over all offsets
+    expanded_rows = []
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
expand dataset window +-1

@@ -26,11 +26,15 @@ def main():
     log.info("Pivoting merged dataset to long format...")
     ws_long = pivot_longer_earnings(ws_link_merged)
 
-    # Save the pivoted dataset directly to the predefined paths
-    ws_long.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    ws_long.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+    # Step 3: Expand dataset for event windows (-1, 0, +1 days)
+    log.info("Expanding dataset for event windows...")
+    ws_expanded = expand_event_window(ws_long)
 
-    log.info(f"Pivoted data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
+    # Save the expanded dataset
+    ws_expanded.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    ws_expanded.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+
+    log.info(f"Expanded data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
 
     log.info("Preparing data for analysis ... Done!")
 
@@ -80,32 +84,33 @@ def pivot_longer_earnings(ws_link_merged):
 
     return ws_long
 
-def expand_event_window(ws_long):
+def expand_event_window(df):
     """
-    Expands the dataset by applying a ±1 day offset to each earnings announcement date.
-    Creates additional rows for Day -1, Day 0, and Day +1.
+    Expands dataset by adding -1, 0, and +1 day event windows for each earnings announcement.
     """
     log.info("Expanding dataset to include event windows (-1, 0, +1 days)...")
 
-    # Define offsets: -1 (before), 0 (announcement day), +1 (after)
+    # Ensure rdq is properly parsed as datetime
+    df["rdq"] = pd.to_datetime(df["rdq"], format="%m/%d/%y", errors="coerce")  
+
+    # Log the number of NaT values before expansion
+    num_nat = df["rdq"].isna().sum()
+    if num_nat > 0:
+        log.warning(f"Found {num_nat} missing or unconvertible 'rdq' values. Skipping these rows.")
+
+    # Drop NaT values to avoid issues in expansion
+    df = df.dropna(subset=["rdq"]).copy()
+
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
merge

@@ -30,11 +30,15 @@ def main():
     log.info("Expanding dataset for event windows...")
     ws_expanded = expand_event_window(ws_long)
 
-    # Save the expanded dataset
-    ws_expanded.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    ws_expanded.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+    # Step 4: Merge with Datastream stock returns
+    log.info("Merging expanded dataset with Datastream stock returns...")
+    final_dataset = merge_with_datastream(ws_expanded, ds2dsf)
 
-    log.info(f"Expanded data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
+    # Save the final dataset
+    final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
+    final_dataset.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
+
+    log.info(f"Final dataset saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV) and {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
 
     log.info("Preparing data for analysis ... Done!")
 
@@ -111,6 +115,27 @@ def expand_event_window(df):
 
     log.info(f"Expanded dataset. New number of rows: {len(df_expanded)}")
     return df_expanded
+
+
+def merge_with_datastream(df_expanded, ds2dsf):
+    """
+    Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`.
+    """
+    log.info("Merging with Datastream stock returns...")
+
+    # Ensure marketdate is in datetime format
+    ds2dsf["marketdate"] = pd.to_datetime(ds2dsf["marketdate"], format="%m/%d/%y", errors="coerce")
+
+    # Merge on `infocode` and `event_date` = `marketdate`
+    df_final = df_expanded.merge(ds2dsf, left_on=["infocode", "event_date"], right_on=["infocode", "marketdate"], how="left")
+
+    # Check for unmatched event dates (missing stock return data)
+    missing_ret_count = df_final["ret"].isna().sum()
+    log.warning(f"{missing_ret_count} rows have missing stock return data. These might be non-trading days.")
+
+    log.info(f"Final merged dataset. Observations: {len(df_final)}")
[…]

### 2025-01-30 code/python/prepare_data-wscp-copy.py
more

@@ -1,228 +1,0 @@
-# --- Header -------------------------------------------------------------------
-# Prepare the pulled data for further analysis as per Task 3 requirements
-#
-# (C) Melisa Mazaeva - See LICENSE file for details
-# ------------------------------------------------------------------------------
-
-import pandas as pd
-from utils import read_config, setup_logging
-
-log = setup_logging()
-
-def main():
-    log.info("Preparing data for analysis ...")
-    cfg = read_config('config/prepare_data_cfg.yaml')
-
-    # Load the pulled datasets
-    ws_stock = pd.read_csv(cfg['worldscope_sample_save_path_csv'])
-    link_ds_ws = pd.read_csv(cfg['link_ds_ws_save_path_csv'])
-    ds2dsf = pd.read_csv(cfg['datastream_sample_save_path_csv'])
-
-    # Step 1: Merge Worldscope with the Linking Table
-    log.info("Merging Worldscope with Linking Table...")
-    ws_link_merged = merge_worldscope_link(ws_stock, link_ds_ws)
-
-    # Step 2: Merge the previous with Datastream data
-    log.info("Merging merged data with Datastream...")
-    final_merged = merge_with_datastream(ws_link_merged, ds2dsf)
-
-    # Step 3: Filter for valid earnings announcement dates
-    log.info("Filtering firm-year observations based on earnings announcement criteria...")
-    final_filtered = filter_valid_earnings(final_merged)
-
-    # Step 4: Match earnings announcements with stock returns
-    final_matched = match_earnings_to_market_dates(final_filtered)
-
-    # Step 5: Compute deviation statistics
-    deviation_stats = compute_deviation_statistics(final_matched)
-
-    # Save the prepared dataset
-    final_matched.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
-    final_matched.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
-
-    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_path']} (CSV)")
-    log.info(f"Prepared data saved to {cfg['prepared_wrds_ds2dsf_parquet']} (Parquet)")
-
-    log.info("Preparing data for analysis ... Done!")
-
-
-def merge_worldscope_link(ws_stock, link_ds_ws):
-    """
-    Merge Worldscope stock data with the linking table.
-    Uses `code` (QA ID for Worldscope) to join with the linking table.
-    """
[…]

### 2025-01-30 code/python/prepare_data-wscp.py

@@ -119,7 +119,8 @@ def expand_event_window(df):
 
 def merge_with_datastream(df_expanded, ds2dsf):
     """
-    Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`.
+    Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`,
+    then drop unnecessary columns and remove rows where merging failed.
     """
     log.info("Merging with Datastream stock returns...")
 
@@ -131,9 +132,17 @@ def merge_with_datastream(df_expanded, ds2dsf):
 
     # Check for unmatched event dates (missing stock return data)
     missing_ret_count = df_final["ret"].isna().sum()
-    log.warning(f"{missing_ret_count} rows have missing stock return data. These might be non-trading days.")
+    log.warning(f"{missing_ret_count} rows have missing stock return data. These will be removed.")
 
-    log.info(f"Final merged dataset. Observations: {len(df_final)}")
+    # Drop rows where `ret` is missing (i.e., the merge was not possible)
+    df_final = df_final.dropna(subset=["ret"]).copy()
+
+    # Drop unnecessary variables after merging
+    drop_columns = ["region", "typecode", "dscode", "marketdate"]  # Also remove redundant `marketdate`
+    df_final = df_final.drop(columns=drop_columns, errors="ignore")
+    log.info(f"Dropped unnecessary columns: {drop_columns}")
+
+    log.info(f"Final merged dataset after dropping unmatched rows. Observations: {len(df_final)}")
     return df_final
 
 

### 2025-01-30 code/python/prepare_data-wscp.py
merge enhance

@@ -90,12 +90,13 @@ def pivot_longer_earnings(ws_link_merged):
 
 def expand_event_window(df):
     """
-    Expands dataset by adding -1, 0, and +1 day event windows for each earnings announcement.
+    Expands dataset by adding -3 to +3 day event windows for each earnings announcement.
+    If `ret = 0` on Day 0, shift `event_date` to the next available trading day.
     """
-    log.info("Expanding dataset to include event windows (-1, 0, +1 days)...")
+    log.info("Expanding dataset to include extended event windows (-3 to +3 days)...")
 
     # Ensure rdq is properly parsed as datetime
-    df["rdq"] = pd.to_datetime(df["rdq"], format="%m/%d/%y", errors="coerce")  
+    df["rdq"] = pd.to_datetime(df["rdq"], format="%m/%d/%y", errors="coerce")
 
     # Log the number of NaT values before expansion
     num_nat = df["rdq"].isna().sum()
@@ -105,8 +106,8 @@ def expand_event_window(df):
     # Drop NaT values to avoid issues in expansion
     df = df.dropna(subset=["rdq"]).copy()
 
-    # Define the event window offsets (-1, 0, +1)
-    offsets = [-1, 0, 1]
+    # Define the extended event window offsets (-3 to +3)
+    offsets = [-3, -2, -1, 0, 1, 2, 3]
 
     # Generate new rows efficiently using pandas repeat + offsets
     df_expanded = df.loc[df.index.repeat(len(offsets))].reset_index(drop=True)
@@ -120,7 +121,7 @@ def expand_event_window(df):
 def merge_with_datastream(df_expanded, ds2dsf):
     """
     Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`,
-    then drop unnecessary columns and remove rows where merging failed.
+    then adjust `event_date` for missing stock returns (`ret = 0`).
     """
     log.info("Merging with Datastream stock returns...")
 
@@ -130,19 +131,29 @@ def merge_with_datastream(df_expanded, ds2dsf):
     # Merge on `infocode` and `event_date` = `marketdate`
     df_final = df_expanded.merge(ds2dsf, left_on=["infocode", "event_date"], right_on=["infocode", "marketdate"], how="left")
 
-    # Check for unmatched event dates (missing stock return data)
-    missing_ret_count = df_final["ret"].isna().sum()
-    log.warning(f"{missing_ret_count} rows have missing stock return data. These will be removed.")
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
again

@@ -131,6 +131,13 @@ def merge_with_datastream(df_expanded, ds2dsf):
     # Merge on `infocode` and `event_date` = `marketdate`
     df_final = df_expanded.merge(ds2dsf, left_on=["infocode", "event_date"], right_on=["infocode", "marketdate"], how="left")
 
+    # Check for unmatched event dates (missing stock return data)
+    missing_ret_count = df_final["ret"].isna().sum()
+    log.warning(f"{missing_ret_count} rows have missing stock return data. These will be removed.")
+
+    # Drop rows where `ret` is missing (i.e., the merge was not possible)
+    df_final = df_final.dropna(subset=["ret"]).copy()
+
     # Identify where `ret = 0` for event window 0
     zero_ret_rows = df_final[(df_final["event_window"] == 0) & (df_final["ret"] == 0)]
     log.info(f"Identified {len(zero_ret_rows)} cases where `ret = 0` on Day 0.")

### 2025-01-30 code/python/prepare_data-wscp.py
dynamic range

@@ -121,7 +121,7 @@ def expand_event_window(df):
 def merge_with_datastream(df_expanded, ds2dsf):
     """
     Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`,
-    then adjust `event_date` for missing stock returns (`ret = 0`).
+    then adjust `event_date` for missing stock returns (`ret = 0`), ensuring continuous shifting.
     """
     log.info("Merging with Datastream stock returns...")
 
@@ -142,18 +142,31 @@ def merge_with_datastream(df_expanded, ds2dsf):
     zero_ret_rows = df_final[(df_final["event_window"] == 0) & (df_final["ret"] == 0)]
     log.info(f"Identified {len(zero_ret_rows)} cases where `ret = 0` on Day 0.")
 
-    # Shift `event_date` to the next available trading day if `ret = 0`
+    # Shift `event_date` continuously until a valid `ret != 0` is found
     for index, row in zero_ret_rows.iterrows():
-        possible_dates = df_final[
-            (df_final["infocode"] == row["infocode"]) & 
-            (df_final["event_date"] > row["event_date"]) & 
-            (df_final["ret"] != 0)
-        ].sort_values(by="event_date")
+        new_date = row["event_date"]
 
-        if not possible_dates.empty:
-            new_date = possible_dates.iloc[0]["event_date"]  # Take the next available trading date
-            df_final.at[index, "event_date"] = new_date
-            df_final.at[index, "ret"] = possible_dates.iloc[0]["ret"]  # Update return value
+        while True:
+            # Get the next available trading date with `ret != 0`
+            possible_dates = df_final[
+                (df_final["infocode"] == row["infocode"]) & 
+                (df_final["event_date"] > new_date) & 
+                (df_final["ret"] != 0)
+            ].sort_values(by="event_date")
+
+            if not possible_dates.empty:
+                new_date = possible_dates.iloc[0]["event_date"]  # Update event_date
+                new_ret = possible_dates.iloc[0]["ret"]
+
+                # Ensure `ret != 0`
+                if new_ret != 0:
+                    df_final.at[index, "event_date"] = new_date
+                    df_final.at[index, "ret"] = new_ret
+                    break  # Exit loop once a valid date is found
+
+            else:
+                log.warning(f"No valid trading day found for infocode {row['infocode']} on {row['event_date']}. Keeping original.")
+                break  # Exit loop if no more valid dates exist
 
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
shift

@@ -122,6 +122,7 @@ def merge_with_datastream(df_expanded, ds2dsf):
     """
     Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`,
     then adjust `event_date` for missing stock returns (`ret = 0`), ensuring continuous shifting.
+    If no valid trading day is found for Day 0, the entire event window (-3 to +3) is dropped.
     """
     log.info("Merging with Datastream stock returns...")
 
@@ -142,9 +143,13 @@ def merge_with_datastream(df_expanded, ds2dsf):
     zero_ret_rows = df_final[(df_final["event_window"] == 0) & (df_final["ret"] == 0)]
     log.info(f"Identified {len(zero_ret_rows)} cases where `ret = 0` on Day 0.")
 
+    # List of infocode & year_ pairs where no valid trading day is found
+    failed_rdq_infocode_pairs = []
+
     # Shift `event_date` continuously until a valid `ret != 0` is found
     for index, row in zero_ret_rows.iterrows():
         new_date = row["event_date"]
+        shifted = False  # Track if shifting was successful
 
         while True:
             # Get the next available trading date with `ret != 0`
@@ -162,11 +167,24 @@ def merge_with_datastream(df_expanded, ds2dsf):
                 if new_ret != 0:
                     df_final.at[index, "event_date"] = new_date
                     df_final.at[index, "ret"] = new_ret
+                    shifted = True  # Mark as shifted
                     break  # Exit loop once a valid date is found
 
             else:
-                log.warning(f"No valid trading day found for infocode {row['infocode']} on {row['event_date']}. Keeping original.")
+                log.warning(f"No valid trading day found for infocode {row['infocode']} on {row['event_date']}. Marking for full window removal.")
+                failed_rdq_infocode_pairs.append((row["infocode"], row["year_"]))
                 break  # Exit loop if no more valid dates exist
+
+    # **NEW STEP: Remove full event windows (-3 to +3) if no valid trading day was found**
+    if failed_rdq_infocode_pairs:
+        log.warning(f"Removing full event windows for {len(failed_rdq_infocode_pairs)} earnings announcements with no valid trading day.")
+
+        # Convert list to DataFrame
+        failed_rdq_df = pd.DataFrame(failed_rdq_infocode_pairs, columns=["infocode", "year_"]).drop_duplicates()
+
+        # Remove all rows associated with these failed announcements
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
dynamic shifting for -1,+1

@@ -139,14 +139,14 @@ def merge_with_datastream(df_expanded, ds2dsf):
     # Drop rows where `ret` is missing (i.e., the merge was not possible)
     df_final = df_final.dropna(subset=["ret"]).copy()
 
-    # Identify where `ret = 0` for event window 0
-    zero_ret_rows = df_final[(df_final["event_window"] == 0) & (df_final["ret"] == 0)]
-    log.info(f"Identified {len(zero_ret_rows)} cases where `ret = 0` on Day 0.")
+    # Identify where `ret = 0` for event windows -1, 0, +1
+    zero_ret_rows = df_final[(df_final["event_window"].isin([-1, 0, 1])) & (df_final["ret"] == 0)]
+    log.info(f"Identified {len(zero_ret_rows)} cases where `ret = 0` in key event windows (-1, 0, +1).")
 
     # List of infocode & year_ pairs where no valid trading day is found
     failed_rdq_infocode_pairs = []
 
-    # Shift `event_date` continuously until a valid `ret != 0` is found
+    # **SHIFTING MECHANISM** - Adjusts Day 0 first, then Day -1 and Day +1 dynamically
     for index, row in zero_ret_rows.iterrows():
         new_date = row["event_date"]
         shifted = False  # Track if shifting was successful

### 2025-01-30 code/python/prepare_data-wscp.py
save

@@ -123,6 +123,7 @@ def merge_with_datastream(df_expanded, ds2dsf):
     Merge expanded dataset with Datastream stock returns using `infocode` and `event_date`,
     then adjust `event_date` for missing stock returns (`ret = 0`), ensuring continuous shifting.
     If no valid trading day is found for Day 0, the entire event window (-3 to +3) is dropped.
+    Finally, removes event windows (-3, -2, +2, +3) as they are no longer needed.
     """
     log.info("Merging with Datastream stock returns...")
 
@@ -186,6 +187,10 @@ def merge_with_datastream(df_expanded, ds2dsf):
         df_final = df_final.merge(failed_rdq_df, on=["infocode", "year_"], how="left", indicator=True)
         df_final = df_final[df_final["_merge"] == "left_only"].drop(columns=["_merge"])
 
+    # **DROP EVENT WINDOWS -3, -2, +2, +3**
+    df_final = df_final[df_final["event_window"].isin([-1, 0, 1])]
+    log.info("Dropped event windows (-3, -2, +2, +3) as they are no longer needed.")
+
     # Drop unnecessary variables after merging
     drop_columns = ["region", "typecode", "dscode", "marketdate"]
     df_final = df_final.drop(columns=drop_columns, errors="ignore")
@@ -196,14 +201,7 @@ def merge_with_datastream(df_expanded, ds2dsf):
 
 
 '''
-def merge_with_datastream(ws_link_merged, ds2dsf):
-    """
-    Merge the Worldscope-linked dataset with Datastream.
-    Uses `infocode` (QA ID for Datastream) as the linking key.
-    """
-    final_merged = ws_link_merged.merge(ds2dsf, on="infocode", how="inner")
-    log.info(f"Merged with Datastream. Final observations: {len(final_merged)}")
-    return final_merged
+
 
 
 def filter_valid_earnings(df):
@@ -292,76 +290,7 @@ def filter_valid_earnings(df):
     return df_filtered
 
 
-def match_earnings_to_market_dates(df):
-    """
-    Match quarterly earnings announcement dates (item5901-4) to market trading dates per firm.
-    Assign the closest available stock return (ret) for each earnings date.
-    """
-
-    log.info("Matching earnings announcements to valid trading days...")
-
-    # Convert 'marketdate' to datetime
-    df["marketdate"] = pd.to_datetime(df["marketdate"], errors="coerce")
-
-    # Filter only necessary columns for efficiency
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
compute

@@ -32,7 +32,11 @@ def main():
 
     # Step 4: Merge with Datastream stock returns
     log.info("Merging expanded dataset with Datastream stock returns...")
-    final_dataset = merge_with_datastream(ws_expanded, ds2dsf)
+    merged_dataset = merge_with_datastream(ws_expanded, ds2dsf)
+
+    # Step 5: Select firms that meet sample criteria
+    log.info("Selecting firms that meet the sample criteria (4 announcements per year)...")
+    final_dataset = select_firms_for_sample(merged_dataset)
 
     # Save the final dataset
     final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
@@ -196,101 +200,56 @@ def merge_with_datastream(df_expanded, ds2dsf):
     df_final = df_final.drop(columns=drop_columns, errors="ignore")
     log.info(f"Dropped unnecessary columns: {drop_columns}")
 
+    # **CHECK FOR DUPLICATES**
+    duplicate_rows = df_final[df_final.duplicated()]
+    num_duplicate_rows = len(duplicate_rows)
+
+    if num_duplicate_rows > 0:
+        log.warning(f"Found {num_duplicate_rows} duplicate rows in the dataset. Displaying the first 5 duplicate rows:")
+        log.warning(f"\n{duplicate_rows.head(5)}")  # Display first 5 duplicate rows
+
+        # Optional: Remove duplicates
+        df_final = df_final.drop_duplicates().reset_index(drop=True)
+        log.info(f"Removed duplicate rows. New dataset size: {len(df_final)}")
+
     log.info(f"Final merged dataset after adjusting `ret = 0`. Observations: {len(df_final)}")
     return df_final
 
 
-'''
-
-
-
-def filter_valid_earnings(df):
+def select_firms_for_sample(df):
     """
-    Filters out firm-year observations where:
-    1. Any of the earnings announcement dates (items 5901-5904) are missing.
-    2. All four earnings announcements must fall within the same calendar year.
-    3. All four earnings announcement dates must be in the year **≤2023**.
-    4. Removes rows where all four earnings announcement dates are identical.
-    Also, identifies the years in `marketdate` where `ret = 0` is most frequent.
+    Filters dataset to retain firms with exactly four earnings announcements per year.
+    Ensures all four announcements fall within the same calendar year and belong to unique quarters (Q1, Q2, Q3, Q4).
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
work

@@ -38,6 +38,12 @@ def main():
     log.info("Selecting firms that meet the sample criteria (4 announcements per year)...")
     final_dataset = select_firms_for_sample(merged_dataset)
 
+    # Step 5: Compute the Buy-and-Hold Returns (BHR)
+    bhr_results = compute_eawr_bhr(final_dataset)
+
+    # Step 6: Save only the BHR results
+    save_bhr_results(bhr_results, cfg)
+
     # Save the final dataset
     final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
     final_dataset.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
@@ -250,7 +256,60 @@ def select_firms_for_sample(df):
 
     return df_filtered
 
+def compute_eawr_bhr(df):
+    """
+    Computes the Earnings Announcement Window Return (EAWR) as the 
+    buy-and-hold return (BHR) over the three-day event window (-1,0,+1).
+    Skips calculations for missing event windows.
+    """
+    log.info("Computing Earnings Announcement Window Returns (3-day BHR)...")
 
+    # Ensure dataset is sorted properly
+    df = df.sort_values(by=["infocode", "rdq", "event_window"])
+
+    # Group by firm and earnings announcement date
+    bhr_results = []
+    
+    for (infocode, rdq), group in df.groupby(["infocode", "rdq"]):
+        # Ensure all required event windows are present
+        if set(group["event_window"]) == {-1, 0, 1}:  
+            try:
+                ret_neg1 = group.loc[group["event_window"] == -1, "ret"].values[0]
+                ret_0 = group.loc[group["event_window"] == 0, "ret"].values[0]
+                ret_1 = group.loc[group["event_window"] == 1, "ret"].values[0]
+
+                # Compute BHR_3day
+                bhr_3day = (1 + ret_neg1) * (1 + ret_0) * (1 + ret_1) - 1
+
+                # Append results
+                bhr_results.append({"infocode": infocode, "rdq": rdq, "BHR_3day": bhr_3day})
+            except Exception as e:
+                log.warning(f"Skipping {infocode} on {rdq} due to missing data: {e}")
+    
+    # Convert to DataFrame
+    df_bhr = pd.DataFrame(bhr_results)
+
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
bhr event

@@ -38,13 +38,15 @@ def main():
     log.info("Selecting firms that meet the sample criteria (4 announcements per year)...")
     final_dataset = select_firms_for_sample(merged_dataset)
 
-    # Step 5: Compute the Buy-and-Hold Returns (BHR)
+    # Step 6: Compute the Buy-and-Hold Returns (BHR)
+    log.info("Computing 3-day Buy-and-Hold Returns (BHR)...")
     bhr_results = compute_eawr_bhr(final_dataset)
 
-    # Step 6: Save only the BHR results
+    # Step 7: Save only the BHR results
+    log.info("Saving BHR results dataset...")
     save_bhr_results(bhr_results, cfg)
 
-    # Save the final dataset
+    # Step 8: Save the final dataset (full dataset with event windows)
     final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
     final_dataset.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
@@ -260,7 +262,7 @@ def compute_eawr_bhr(df):
     """
     Computes the Earnings Announcement Window Return (EAWR) as the 
     buy-and-hold return (BHR) over the three-day event window (-1,0,+1).
-    Skips calculations for missing event windows.
+    Retains the `quarter` column from the original dataset.
     """
     log.info("Computing Earnings Announcement Window Returns (3-day BHR)...")
 
@@ -271,45 +273,55 @@ def compute_eawr_bhr(df):
     bhr_results = []
     
     for (infocode, rdq), group in df.groupby(["infocode", "rdq"]):
-        # Ensure all required event windows are present
+        # Ensure all required event windows (-1, 0, +1) are present
         if set(group["event_window"]) == {-1, 0, 1}:  
             try:
                 ret_neg1 = group.loc[group["event_window"] == -1, "ret"].values[0]
                 ret_0 = group.loc[group["event_window"] == 0, "ret"].values[0]
                 ret_1 = group.loc[group["event_window"] == 1, "ret"].values[0]
 
+                # Retrieve quarter information (same across event window)
+                quarter = group["quarter"].iloc[0]  
+
                 # Compute BHR_3day
                 bhr_3day = (1 + ret_neg1) * (1 + ret_0) * (1 + ret_1) - 1
 
-                # Append results
-                bhr_results.append({"infocode": infocode, "rdq": rdq, "BHR_3day": bhr_3day})
[…]

### 2025-01-30 code/python/prepare_data-wscp.py
saveeee

@@ -38,13 +38,8 @@ def main():
     log.info("Selecting firms that meet the sample criteria (4 announcements per year)...")
     final_dataset = select_firms_for_sample(merged_dataset)
 
-    # Step 6: Compute the Buy-and-Hold Returns (BHR)
-    log.info("Computing 3-day Buy-and-Hold Returns (BHR)...")
-    bhr_results = compute_eawr_bhr(final_dataset)
-
-    # Step 7: Save only the BHR results
-    log.info("Saving BHR results dataset...")
-    save_bhr_results(bhr_results, cfg)
+    # Step 6: Compute and Save BHR (Event Window)
+    bhr_event_results = compute_and_save_eawr_bhr(final_dataset, cfg)
 
     # Step 8: Save the final dataset (full dataset with event windows)
     final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
@@ -258,13 +253,13 @@ def select_firms_for_sample(df):
 
     return df_filtered
 
-def compute_eawr_bhr(df):
+def compute_and_save_eawr_bhr(df, cfg):
     """
     Computes the Earnings Announcement Window Return (EAWR) as the 
     buy-and-hold return (BHR) over the three-day event window (-1,0,+1).
-    Retains the `quarter` column from the original dataset.
+    Retains the `quarter` column and saves the output directly to CSV & Parquet.
     """
-    log.info("Computing Earnings Announcement Window Returns (3-day BHR)...")
+    log.info("Computing and saving Earnings Announcement Window Returns (3-day BHR)...")
 
     # Ensure dataset is sorted properly
     df = df.sort_values(by=["infocode", "rdq", "event_window"])
@@ -300,28 +295,23 @@ def compute_eawr_bhr(df):
     df_bhr = pd.DataFrame(bhr_results)
 
     log.info(f"Computed {len(df_bhr)} earnings announcement window returns. Quarter column is retained.")
-    return df_bhr
 
-
-def save_bhr_results(df_bhr, cfg):
-    """
-    Saves the computed BHR_3day dataset to CSV and Parquet formats.
-    Ensures the `quarter` column is retained.
-    """
-    log.info("Saving BHR dataset...")
-
+    # **SAVE THE OUTPUT**
     # Keep only relevant columns (Include `quarter` for regression use)
[…]

### 2025-01-31 doc/paper.qmd
expand dataset window +-1
annual stock data

--- 2025-01-30 doc/paper.qmd
@@
 
-7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure the inclusion of trading days around earnings announcements.
-
 ## Replication Steps {#sec-replication_steps3}
@@
 and Canada.
+
+Notably, after pulling the annual stock data for further annual return calculation, all infocodes present an average of 250 trading days, highlighting full year stock coverage.
 

### 2025-01-31 code/python/prepare_data-wscp.py

@@ -41,6 +41,9 @@ def main():
     # Step 6: Compute and Save BHR (Event Window)
     bhr_event_results = compute_and_save_eawr_bhr(final_dataset, cfg)
 
+    # Step 7: Extract annual stock return data for firms in BHR Event dataset
+    annual_stock_data = extract_annual_stock_data(bhr_event_results, ds2dsf, cfg)
+
     # Step 8: Save the final dataset (full dataset with event windows)
     final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
     final_dataset.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
@@ -296,7 +299,7 @@ def compute_and_save_eawr_bhr(df, cfg):
 
     log.info(f"Computed {len(df_bhr)} earnings announcement window returns. Quarter column is retained.")
 
-    # **SAVE THE OUTPUT**
+    # SAVE THE OUTPUT
     # Keep only relevant columns (Include `quarter` for regression use)
     df_bhr_filtered = df_bhr[["infocode", "rdq", "quarter", "BHR_3day"]]
 
@@ -312,6 +315,70 @@ def compute_and_save_eawr_bhr(df, cfg):
 
     return df_bhr
 
+def extract_annual_stock_data(bhr_event_results, ds2dsf, cfg):
+    """
+    Extracts annual stock return data for firms present in the BHR Event dataset.
+    Ensures that stock data only contains the same infocodes and years as in BHR Event.
+    Saves the filtered dataset for computing annual buy-and-hold returns.
+    """
+    log.info("Extracting annual stock return data...")
+
+    ## Extract Unique Firms & Years from BHR Event Dataset
+    selected_firms = bhr_event_results[["infocode", "rdq"]].copy()
+    selected_firms["year_bhr"] = pd.to_datetime(selected_firms["rdq"]).dt.year  # Extract year from `rdq`
+    # Drop duplicates to ensure unique firm-year pairs
+    selected_firms = selected_firms.drop_duplicates(subset=["infocode", "year_bhr"])  
+    log.info(f"Selected {len(selected_firms)} unique firm-year pairs from BHR Event dataset.")
+    log.info(f"Sample of firm-year pairs:\n{selected_firms.head(20).to_string()}")
+
+    ## Load Full Stock Dataset (Unfiltered Datastream Data)
[…]

### 2025-01-31 code/python/prepare_data-wscp.py
prepare final

@@ -44,7 +44,10 @@ def main():
     # Step 7: Extract annual stock return data for firms in BHR Event dataset
     annual_stock_data = extract_annual_stock_data(bhr_event_results, ds2dsf, cfg)
 
-    # Step 8: Save the final dataset (full dataset with event windows)
+    # Step 8: Compute and Save BHR (Annual Return)
+    bhr_annual_results = compute_and_save_annual_bhr(cfg)
+
+    # Step 9: Save the final dataset (full dataset with event windows)
     final_dataset.to_csv(cfg['prepared_wrds_ds2dsf_path'], index=False)
     final_dataset.to_parquet(cfg['prepared_wrds_ds2dsf_parquet'], index=False)
 
@@ -379,6 +382,68 @@ def extract_annual_stock_data(bhr_event_results, ds2dsf, cfg):
     log.info(f"Annual stock data saved to:\n- {annual_stock_csv_path} (CSV)\n- {annual_stock_parquet_path} (Parquet).")
 
     return filtered_stock_data
+
+def compute_and_save_annual_bhr(cfg):
+    """
+    Computes the Annual Buy-and-Hold Return (BHR_Annual) using daily stock returns.
+    Retains the `year_stock` column and saves the output directly to CSV & Parquet.
+    """
+    log.info("Computing and saving Annual Buy-and-Hold Returns (BHR_Annual)...")
+
+    # Load the filtered annual stock data
+    annual_stock_data = pd.read_csv(cfg["annual_stock_data_csv"])
+    log.info(f"Loaded annual stock data. Total records: {len(annual_stock_data)}")
+
+    # Ensure `marketdate` is in datetime format
+    annual_stock_data["marketdate"] = pd.to_datetime(annual_stock_data["marketdate"], errors="coerce")
+
+    # Sort data for correct computation order
+    annual_stock_data = annual_stock_data.sort_values(by=["infocode", "year_stock", "marketdate"])
+
+    # Verify available years
+    log.info("Sample of available years in the dataset:")
+    log.info(annual_stock_data["year_stock"].value_counts().sort_index())
+
+    # Compute Buy-and-Hold Annual Return (BHR_Annual)
+    bhr_annual_results = []
+
+    for (infocode, year_stock), group in annual_stock_data.groupby(["infocode", "year_stock"]):
+        try:
+            # Ensure sorted data for proper calculation
+            group = group.sort_values(by="marketdate")
+
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
do analysis

@@ -1,1 +1,92 @@
-## TAKE A LOOK AT SS24
+# We start by loading the libraries that we will use in this analysis.
+import os
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import read_config, setup_logging
+
+# Set up logging
+log = setup_logging()
+
+def main():
+    log.info("Starting analysis ...")
+    cfg = read_config('config/prepare_data_cfg.yaml')
+
+    # Load datasets
+    log.info("Loading computed BHR Event and BHR Annual datasets...")
+    bhr_event_results = pd.read_csv(cfg["bhr_event_output_csv"])
+    bhr_annual_results = pd.read_csv(cfg["bhr_annual_output_csv"])
+
+    # Compute summary statistics
+    df_summary = compute_summary_statistics(bhr_annual_results, bhr_event_results)
+
+
+
+    log.info("Analysis complete.")
+
+def compute_summary_statistics(bhr_annual_results, bhr_event_results):
+    """
+    Computes summary statistics (Mean, Median, Skewness, % Obs = 0, % Obs > 0) 
+    for annual and earnings-announcement window returns.
+    """
+    log.info("Computing summary statistics for comparison with Table 1...")
+
+    # **Annual Returns Summary**
+    annual_stats = {
+        "Category": "Calendar-Year Returns",
+        "No. Obs.": len(bhr_annual_results),
+        "Mean": np.mean(bhr_annual_results["BHR_Annual"]),
+        "Median": np.median(bhr_annual_results["BHR_Annual"]),
+        "Skewness": pd.Series(bhr_annual_results["BHR_Annual"]).skew(),
+        "% Obs. = 0": np.mean(bhr_annual_results["BHR_Annual"] == 0) * 100,
+        "% Obs. > 0": np.mean(bhr_annual_results["BHR_Annual"] > 0) * 100,
+    }
+
+    # **Earnings-Announcement Window Summary (for each quarter)**
+    quarterly_stats = []
+    for q in ["Q1", "Q2", "Q3", "Q4"]:
+        df_q = bhr_event_results[bhr_event_results["quarter"] == q]
+
+        q_stats = {
+            "Category": f"Earnings-Announcement Window Returns in {q}",
+            "No. Obs.": len(df_q),
+            "Mean": np.mean(df_q["BHR_3day"]),
+            "Median": np.median(df_q["BHR_3day"]),
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
regression

@@ -2,7 +2,8 @@
 import os
 import pandas as pd
 import numpy as np
-import matplotlib.pyplot as plt
+import matplotlib.pyplot as plt#
+import statsmodels.api as sm
 from utils import read_config, setup_logging
 
 # Set up logging
@@ -20,14 +21,22 @@ def main():
     # Compute summary statistics
     df_summary = compute_summary_statistics(bhr_annual_results, bhr_event_results)
 
+    # Run annual regressions
+    df_regression = run_regressions(bhr_annual_results, bhr_event_results)
 
+    # Save regression results
+    regression_output_csv = cfg["regression_output_csv"]
+    df_regression.to_csv(regression_output_csv, index=False)
+
+    log.info(f"Regression results saved to {regression_output_csv}")
 
     log.info("Analysis complete.")
 
 def compute_summary_statistics(bhr_annual_results, bhr_event_results):
     """
     Computes summary statistics (Mean, Median, Skewness, % Obs = 0, % Obs > 0) 
-    for annual and earnings-announcement window returns.
+    for annual returns and earnings-announcement window returns like in Table 1 by Ball(2008)
+    to compare preliminary results.
     """
     log.info("Computing summary statistics for comparison with Table 1...")
 
@@ -67,26 +76,65 @@ def compute_summary_statistics(bhr_annual_results, bhr_event_results):
 
     return df_summary
 
-def plot_summary_statistics(df_summary):
+def run_regressions(bhr_annual, bhr_event):
     """
-    Plots a bar chart comparing our computed summary statistics with Ball (2008) Table 1.
+    Performs annual cross-sectional regressions of calendar-year returns on 
+    the four earnings-announcement window returns in the calendar year.
+    Replicates Table 2 in Ball (2008).
     """
-    log.info("Plotting summary statistics for comparison with Ball’s Table 1...")
 
-    fig, ax = plt.subplots(figsize=(10, 6))
-    df_summary.set_index("Category")[["Mean", "Median", "Skewness"]].plot(kind="bar", ax=ax)
-    
-    plt.title("Comparison of Summary Statistics (Our Results vs. Ball Table 1)")
-    plt.ylabel("Value")
-    plt.xticks(rotation=45, ha="right")
-    plt.tight_layout()
+    log.info("Running annual regressions (Table 2 format)...")
+    regression_results = []
 
-    # Save figure
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
regression run

@@ -21,14 +21,23 @@ def main():
     # Compute summary statistics
     df_summary = compute_summary_statistics(bhr_annual_results, bhr_event_results)
 
+    # Save summary statistics
+    summary_statistics_csv = cfg["summary_statistics_csv"]
+    df_summary.to_csv(summary_statistics_csv, index=False)
+    log.info(f"Summary statistics saved to {summary_statistics_csv}")
+
     # Run annual regressions
     df_regression = run_regressions(bhr_annual_results, bhr_event_results)
 
-    # Save regression results
-    regression_output_csv = cfg["regression_output_csv"]
-    df_regression.to_csv(regression_output_csv, index=False)
+    # Save regression results (CSV)
+    regression_results_csv = cfg["regression_results_csv"]
+    df_regression.to_csv(regression_results_csv, index=False)
+    log.info(f"Regression results saved to {regression_results_csv}")
 
-    log.info(f"Regression results saved to {regression_output_csv}")
+    '''    # Save regression plot
+    regression_plot_path = cfg["regression_results_plot"]
+    plt.savefig(regression_plot_path) 
+    log.info(f"Regression plot saved to {regression_plot_path}")'''
 
     log.info("Analysis complete.")
 
@@ -84,13 +93,22 @@ def run_regressions(bhr_annual, bhr_event):
     """
 
     log.info("Running annual regressions (Table 2 format)...")
-    regression_results = []
 
-    # Ensure data is merged correctly
+    # **Ensure `year_stock` column exists in BHR Event dataset**
+    if "year_stock" not in bhr_event.columns:
+        bhr_event["year_stock"] = pd.to_datetime(bhr_event["rdq"]).dt.year
+        log.info("Added `year_stock` column to BHR Event dataset.")
+
+    # Print column names for debugging
+    log.info(f"BHR Annual Columns: {bhr_annual.columns.tolist()}")
+    log.info(f"BHR Event Columns: {bhr_event.columns.tolist()}")
+
+    # Merge datasets correctly
     merged_data = bhr_annual.merge(bhr_event, on=["infocode", "year_stock"], how="inner")
     log.info(f"Merged dataset for regression. Total observations: {len(merged_data)}")
 
     # Run regressions for each year
+    regression_results = []
     for year in sorted(merged_data["year_stock"].unique()):
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
regressions

@@ -11,7 +11,7 @@ log = setup_logging()
 
 def main():
     log.info("Starting analysis ...")
-    cfg = read_config('config/prepare_data_cfg.yaml')
+    cfg = read_config('config/do_analysis_cfg.yaml')
 
     # Load datasets
     log.info("Loading computed BHR Event and BHR Annual datasets...")
@@ -112,26 +112,34 @@ def run_regressions(bhr_annual, bhr_event):
     for year in sorted(merged_data["year_stock"].unique()):
         yearly_data = merged_data[merged_data["year_stock"] == year]
 
-        # Ensure each firm has all four quarters
-        firm_counts = yearly_data.groupby("infocode")["quarter"].nunique()
-        valid_firms = firm_counts[firm_counts == 4].index
-        yearly_data = yearly_data[yearly_data["infocode"].isin(valid_firms)]
-
-        if len(yearly_data) < 10:  # Skip years with too few firms
-            log.warning(f"Skipping year {year} due to insufficient data ({len(yearly_data)} firms).")
-            continue
-
         # Pivot data to have Q1, Q2, Q3, Q4 as separate columns
-        yearly_pivot = yearly_data.pivot_table(index=["infocode", "year_stock"], columns="quarter", values="BHR_3day").reset_index()
-        yearly_pivot = yearly_pivot.rename(columns={"Q1": "BHR_Q1", "Q2": "BHR_Q2", "Q3": "BHR_Q3", "Q4": "BHR_Q4"})
+        yearly_pivot = yearly_data.pivot_table(
+            index=["infocode", "year_stock"], 
+            columns="quarter", 
+            values="BHR_3day"
+        ).reset_index()
+
+        # Rename columns for clarity
+        yearly_pivot = yearly_pivot.rename(
+            columns={"Q1": "BHR_Q1", "Q2": "BHR_Q2", "Q3": "BHR_Q3", "Q4": "BHR_Q4"}
+        )
 
         # Merge back with annual returns
         final_data = yearly_pivot.merge(bhr_annual, on=["infocode", "year_stock"], how="inner")
 
         # Define Dependent and Independent Variables
-        X = final_data[["BHR_Q1", "BHR_Q2", "BHR_Q3", "BHR_Q4"]]
+        independent_vars = ["BHR_Q1", "BHR_Q2", "BHR_Q3", "BHR_Q4"]
+        X = final_data[independent_vars]
         y = final_data["BHR_Annual"]
+
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
regression

@@ -87,25 +87,19 @@ def compute_summary_statistics(bhr_annual_results, bhr_event_results):
 
 def run_regressions(bhr_annual, bhr_event):
     """
-    Performs annual cross-sectional regressions of calendar-year returns on 
+    Runs annual cross-sectional regressions of calendar-year returns on 
     the four earnings-announcement window returns in the calendar year.
     Replicates Table 2 in Ball (2008).
     """
 
-    log.info("Running annual regressions (Table 2 format)...")
+    log.info("Running annual regressions (Fixed Version)...")
 
-    # **Ensure `year_stock` column exists in BHR Event dataset**
+    # Ensure `year_stock` column exists in BHR Event dataset
     if "year_stock" not in bhr_event.columns:
         bhr_event["year_stock"] = pd.to_datetime(bhr_event["rdq"]).dt.year
-        log.info("Added `year_stock` column to BHR Event dataset.")
 
-    # Print column names for debugging
-    log.info(f"BHR Annual Columns: {bhr_annual.columns.tolist()}")
-    log.info(f"BHR Event Columns: {bhr_event.columns.tolist()}")
-
-    # Merge datasets correctly
+    # Merge annual and event datasets
     merged_data = bhr_annual.merge(bhr_event, on=["infocode", "year_stock"], how="inner")
-    log.info(f"Merged dataset for regression. Total observations: {len(merged_data)}")
 
     # Run regressions for each year
     regression_results = []
@@ -132,9 +126,18 @@ def run_regressions(bhr_annual, bhr_event):
         X = final_data[independent_vars]
         y = final_data["BHR_Annual"]
 
-        # **Handle missing quarters by filling NaN with 0** (otherwise regression may fail)
-        X = X.fillna(0)
+        # **Fix Missing Values in Independent Variables**
+        X = X.fillna(0)  # Replace NaNs with 0
         X = sm.add_constant(X)  # Add intercept
+
+        # **Check for NaNs or Infs in y or X**
+        if X.isna().any().any() or y.isna().any():
+            log.warning(f"Skipping year {year} due to NaNs in data.")
+            continue
+
+        if np.isinf(X).any().any() or np.isinf(y).any():
+            log.warning(f"Skipping year {year} due to Inf values in data.")
+            continue
 
         # Skip regression if no valid data is left
         if X.shape[0] < 2:  
@@ -156,11 +159,7 @@ def run_regressions(bhr_annual, bhr_event):
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
benchmarking added

@@ -89,10 +89,10 @@ def run_regressions(bhr_annual, bhr_event):
     """
     Runs annual cross-sectional regressions of calendar-year returns on 
     the four earnings-announcement window returns in the calendar year.
-    Replicates Table 2 in Ball (2008).
+    Computes Adjusted R² and Abnormal R², following Ball (2008).
     """
 
-    log.info("Running annual regressions (Fixed Version)...")
+    log.info("Running annual regressions with Abnormal R² benchmarking...")
 
     # Ensure `year_stock` column exists in BHR Event dataset
     if "year_stock" not in bhr_event.columns:
@@ -139,13 +139,17 @@ def run_regressions(bhr_annual, bhr_event):
             log.warning(f"Skipping year {year} due to Inf values in data.")
             continue
 
-        # Skip regression if no valid data is left
-        if X.shape[0] < 2:  
-            log.warning(f"Skipping year {year} due to insufficient data ({X.shape[0]} observations).")
+        # **Ensure we have enough observations for valid regression**
+        if X.shape[0] <= X.shape[1]:  
+            log.warning(f"Skipping year {year} due to insufficient observations (n={X.shape[0]}, k={X.shape[1] - 1}).")
             continue
 
         # Fit Regression Model
         model = sm.OLS(y, X).fit()
+
+        # Compute Adjusted R² & Abnormal R²
+        adj_r2 = model.rsquared_adj if model.nobs > model.df_model + 1 else np.nan
+        abnormal_r2 = adj_r2 - 0.048 if not np.isnan(adj_r2) else np.nan
 
         # Store results
         regression_results.append({
@@ -155,11 +159,23 @@ def run_regressions(bhr_annual, bhr_event):
             "Q2": model.params.get("BHR_Q2", np.nan),
             "Q3": model.params.get("BHR_Q3", np.nan),
             "Q4": model.params.get("BHR_Q4", np.nan),
-            "Adj_R²": model.rsquared_adj,
+            "Adj_R²": adj_r2,
+            "Abnormal R²": abnormal_r2,  # New column
             "No. Obs.": len(final_data)
         })
 
-    return pd.DataFrame(regression_results)
+    results_df = pd.DataFrame(regression_results)
+
+    # **Fill NaN Adj_R² with a marker (-999) if needed**
+    results_df["Adj_R²"] = results_df["Adj_R²"].fillna(-999)
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
plot

@@ -34,11 +34,10 @@ def main():
     df_regression.to_csv(regression_results_csv, index=False)
     log.info(f"Regression results saved to {regression_results_csv}")
 
-    '''    # Save regression plot
-    regression_plot_path = cfg["regression_results_plot"]
-    plt.savefig(regression_plot_path) 
-    log.info(f"Regression plot saved to {regression_plot_path}")'''
+    # Generate Figure 1 replication
+    plot_figure1(df_regression, cfg["figure1_save_path"], cfg['figure1_pickle_path'])
 
+    
     log.info("Analysis complete.")
 
 def compute_summary_statistics(bhr_annual_results, bhr_event_results):
@@ -175,6 +174,46 @@ def run_regressions(bhr_annual, bhr_event):
 
     return results_df
 
+def plot_figure1(results_df, save_path, pickle_path):
+    """
+    Replicates Figure 1 from Ball (2008), including:
+    - Panel A: Abnormal Adjusted R² over time
+    - Panel B: Slope Coefficients for Q1, Q2, Q3, Q4 over time
+    """
+
+    log.info("Generating Figure 1 replication...")
+
+    # **Panel A: Abnormal Adjusted R²**
+    plt.figure(figsize=(10, 8))
+
+    plt.subplot(2, 1, 1)  # 2 rows, 1 column, 1st subplot
+    abnormal_r2 = results_df["Abnormal R²"] * 100  # Convert to percentage
+    plt.plot(results_df["Year"], abnormal_r2, marker="o", linestyle="-", color="black")
+    plt.axhline(y=0, color="gray", linestyle="--")
+    plt.xlabel("Year")
+    plt.ylabel("Abnormal Adj. R² (%)")
+    plt.title("Panel A: Abnormal Adjusted R² Over Time")
+    plt.grid(True)
+
+    # **Panel B: Slope Coefficients**
+    plt.subplot(2, 1, 2)  # 2 rows, 1 column, 2nd subplot
+    plt.plot(results_df["Year"], results_df["Q1"], label="Quarter 1", linestyle="dashed", color="black")
+    plt.plot(results_df["Year"], results_df["Q2"], label="Quarter 2", linestyle="solid", color="gray")
+    plt.plot(results_df["Year"], results_df["Q3"], label="Quarter 3", linestyle="dotted", color="black")
[…]

### 2025-01-31 code/python/do_analysis-wscp.py
figure adjust

@@ -1,8 +1,9 @@
 # We start by loading the libraries that we will use in this analysis.
 import os
+import pickle
 import pandas as pd
 import numpy as np
-import matplotlib.pyplot as plt#
+import matplotlib.pyplot as plt
 import statsmodels.api as sm
 from utils import read_config, setup_logging
 
@@ -175,45 +176,56 @@ def run_regressions(bhr_annual, bhr_event):
     return results_df
 
 def plot_figure1(results_df, save_path, pickle_path):
-    """
-    Replicates Figure 1 from Ball (2008), including:
-    - Panel A: Abnormal Adjusted R² over time
-    - Panel B: Slope Coefficients for Q1, Q2, Q3, Q4 over time
-    """
+    """Replicates Figure 1 from Ball (2008) and saves it as PNG and Pickle."""
 
     log.info("Generating Figure 1 replication...")
 
-    # **Panel A: Abnormal Adjusted R²**
-    plt.figure(figsize=(10, 8))
+    # Create figure
+    fig, axes = plt.subplots(2, 1, figsize=(10, 8), gridspec_kw={'height_ratios': [1, 1]})
 
-    plt.subplot(2, 1, 1)  # 2 rows, 1 column, 1st subplot
-    abnormal_r2 = results_df["Abnormal R²"] * 100  # Convert to percentage
-    plt.plot(results_df["Year"], abnormal_r2, marker="o", linestyle="-", color="black")
-    plt.axhline(y=0, color="gray", linestyle="--")
-    plt.xlabel("Year")
-    plt.ylabel("Abnormal Adj. R² (%)")
-    plt.title("Panel A: Abnormal Adjusted R² Over Time")
-    plt.grid(True)
+    # **Panel A: Abnormal Adjusted R²**
+    abnormal_r2 = results_df["Abnormal R²"] * 100  
+    axes[0].plot(results_df["Year"], abnormal_r2, marker="o", linestyle="-", color="black")
+    axes[0].axhline(y=0, color="gray", linestyle="--")
+    axes[0].set_xlabel("Year")
+    axes[0].set_ylabel("Abnormal Adj. R² (%)")
+    axes[0].set_title("Panel A: Abnormal adjusted R² values from annual cross-sectional regressions\n"
+                      "calendar-year arithmetic returns on arithmetic returns\n"
+                      "at the four quarterly earnings announcements")
+    axes[0].grid(True)
 
     # **Panel B: Slope Coefficients**
[…]

### 2025-01-31 doc/paper.qmd
more

@@
   | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide infrastructure for open science-oriented empirical projects.
-Leveraging data from the CRSP and Compustat databases via WRDS, alongside Worldscope and Datastream via Thomson/Refinitiv, this repository showcases a reproducible workflow integrating Python scripts for data preparation, analysis, and visualization.
+Leveraging data from the CRSP and Compustat databases, alongside Worldscope and Datastream via WRDS, this repository showcases a reproducible workflow integrating Python scripts for data preparation, analysis, and visualization.
 Integrating multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
-The project replicates and extends Ball and Shivakumar (2008) to analyze the informativeness of quarterly earnings announcements and their contribution to annual share price movements, highlighting their critical role in investment decisions and impact on investors, analysts, and policymakers.
+The project replicates and extends Ball and Shivakumar (2008) to analyze the informativeness of quarterly earnings announcements and their contribution to share price movements, highlighting their critical role in investment decisions and impact on investors and analysts.
 Key tasks include replicating and comparing original results, extending the analysis to 2007–2023, and applying the methodology to a non-U.S.
@@
 Assignment II explored the economic implications of corporate financial reporting, focusing on @graham_economic_2005 to analyze managerial decision-making, earnings management strategies, and voluntary disclosure practices.
-This study highlighted the trade-offs between short-term earnings predictability and long-term firm value and provided a foundation for understanding corporate incentives in financial reporting.
 
@@
 The project replicates and extends @ball_how_2008, assessing the extent to which earnings releases serve as a source of new information for financial markets.
-By integrating multiple datasets from WRDS and applying an event-study methodology, this study evaluates the economic role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting.
+By integrating multiple datasets from WRDS and applying an event-study methodology, this study aims to evaluate the role of earnings disclosures in market efficiency, showcasing the valuation purpose of accounting.
 At the same time, earnings reports may play a crucial role in contracting by influencing managerial compensation, debt agreements, and other contractual mechanisms tied to financial performance [@ball_how_2008].
 The integration of multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.
-Key tasks include replicating and comparing original results, extending the analysis to data from 2007–2023, and applying the methodology to Canada as a non-U.S.
-country to explore cross-market variations.
 
@@
 Additionally, it sketches a research design for a non-archival study to evaluate the paper’s findings through an alternative methodological lens.
-This project leverages the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to establish an open science-oriented infrastructure, ensuring transparency, replicability, and structured workflows for empirical accounting research.
+This project leverages the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to establish an open science-oriented infrastructure, ensuring transparency and replicability for empirical accounting research.
 
-Earnings announcements provide investors with valuable information about a firm’s market value, with stock prices reacting significantly when earnings news deviates from expectations [@fink_review_2021, p.2].
+Earnings announcements provide investors with valuable information about a firm’s market value, with stock prices reacting significantly when earnings news deviate from expectations [@fink_review_2021, p.2].
 The seminal study by @ball_empirical_1968 was the first to document this relationship, showing that stock prices anticipate earnings surprises, with most of the market reaction occurring before the official announcement, suggesting that earnings reports primarily confirm rather than introduce new information.
 Over the past decades, more than a thousand studies have examined the interplay between capital markets and financial statements, a research stream that originated with Ball and Brown (1968)  [@kothari_capital_2001].
-This reinforces the role of earnings announcements as a crucial source of financial information.
 
@@
 By estimating the R² from regressions of annual stock returns on earnings announcement window returns, the paper quantifies the informativeness of earnings releases, finding that they account for only 1% to 2% of total annual volatility.
-This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting, reinforcing prior market expectations rather than acting as a primary source of new insights.
-Their findings align with the semi-strong form of market efficiency, which suggests that stock prices already reflect all publicly available information, including prior signals about earnings.
+This challenges the assumption that earnings provide substantial new information and instead suggests a confirmatory role in financial reporting.
+These findings align with the semi-strong form of market efficiency, which suggests that stock prices already reflect all publicly available information, including prior signals about earnings.
 Unlike traditional event studies that assume market efficiency, @ball_how_2008 allow for potential market mispricing by not imposing a unit slope restriction in their regressions, meaning that their approach can capture under- or overreaction to earnings announcements.
 They also emphasize that extending the event window beyond the earnings announcement period would shift the research focus from earnings “surprise” to broader financial reporting effects, such as its role in debt contracting and executive compensation.
-The study further documents an increasing trend in earnings informativeness in recent years, potentially linked to regulatory changes, shifts in analyst activity, or broader market conditions.
 
@@
 Moreover, the extent to which earnings informativeness varies across international markets remains underexplored.
-By replicating their study with updated data from 2007–2023 and applying the methodology to a non-U.S.
-country, this project reassesses the robustness of their findings, examines long-term trends, and evaluates cross-country differences in earnings informativeness.
-Through this approach, it critically evaluates the generalizability of the original results and provides further insights into the economic role of earnings announcements in financial markets, offering a contemporary perspective on their evolving informativeness and implications for investors, analysts, and policymakers.
+By replicating their study with updated data from 2007–2023 and applying the methodology to Canada as a non-U.S.
+country, this project reassesses the robustness of their findings.
+Through this approach, it critically evaluates the generalizability of the original results.
 
-The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment.
+The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps and results.
 @sec-task1 follows an exact replication approach by replicating key tables and figures from the original study using US data (1972–2006) to establish baseline results.
@@
 The concluding remarks are provided in @sec-conclusion.
-The entire Python computation code for regression run is available in `code/python/do_analysis.py` and `code/python/do_analysis-wscp.py` for detailed review if necessary.
-This paper focuses on the replication process, presenting visualizations, and discussing the results.
 

### 2025-01-31 doc/paper.qmd
comm

@@
 
+```{python}
+#| label: fig-abnormal-r2
+#| fig-cap: "Replicated Figure 1: Abnormal Adjusted R² Values and Slope Coefficients from Annual Regressions"
+#| fig-align: center
+#| echo: false
+
+import pickle
+import matplotlib.pyplot as plt
+
+# Load the figure from the pickle file
+with open('../output/figure1_replication.pickle', 'rb') as f:
+    fig = pickle.load(f)
+
+# Render the figure explicitly
+plt.figure(fig.number)
+plt.show()
+```
+
 # Task 4 - Research Design for a Non-Archival Study {#sec-task4}

### 2025-01-31 doc/paper.qmd
paper upd

--- 2025-01-31 doc/paper.qmd
@@
 Task 1 is the most comprehensive, replicating the methodology of key tables and figures from @ball_how_2008 using daily US stock return data (1972–2006) to establish baseline results, ensuring alignment with the original findings before extending the analysis in @sec-task2.
-By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), this task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.
+By reconstructing Table 1 (Panel A), Table 2 (all panels), and Figure 1 (all panels), the task evaluates the robustness of the original results and identifies potential discrepancies, offering insights into data consistency, methodology, and market dynamics over the examined period.
 The use of daily CRSP data is essential for capturing short-term stock price movements around earnings announcements, ensuring precise event window calculations.
@@
 Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window.
-This adjustment prevents shortening the window, ensuring a complete three-day period for capturing the full market response to earnings announcements.
 
@@
 The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually).
-Timing mismatches may arise, especially for firms with restated financials, leading to slight variations in event window alignment when calculating earnings-announcement returns.
-Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause minor differences in firm coverage or reported values.
+Timing mismatches may arise, especially for firms with restated financials, leading to possible variations in event window alignment when calculating earnings-announcement returns.
+Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause differences in firm coverage or reported values.
 
@@
 
-By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I successfully replicated the results from @ball_how_2008.
+By following the steps outlined in @sec-replication_steps1 and adhering to the assumptions made, I aim to replicate the results from @ball_how_2008.
 A thorough step-by-step approach, with each step clearly documented, helps to understand and verify the outputs.
@@
 **Step 1: Pulling the Data and Managing the Databases**  
-Data is pulled from the `crsp_a_ccm.ccmxpf_lnkhist`, `crsp_a_stock.dsf`, `comp_na_daily_all.fundq` tables via WRDS, using Python for data processing and regression analysis and facilitating direct access to stock price and return data from CRSP alongside firm fundamentals from Compustat, enabling a seamless link between market and accounting data.
-Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.
+Data is pulled from WRDS using Python to integrate daily stock returns from CRSP (`crsp_a_stock.dsf`) with quarterly earnings announcement data from Compustat (`comp_na_daily_all.fundq`), linked via the Compustat-CRSP link table (`crsp_a_ccm.ccmxpf_lnkhist`).
+`permno` identifier matches stock returns to firm fundamentals via `gvkey` for exact firm/year match.
+Key variables include `ret` (daily stock return) and `rdq` (earnings announcement date), enabling event study analysis from 1972 to 2023.
 While WRDS provides extensive financial datasets, documentation on precise variable selection and dataset integration is limited, requiring additional validation and cross-referencing with prior research.
 
-This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.
-
-To ensure data relevance, the pulling process was restricted to data for the year 2021.
-The variable `trans_report_auditor_state` was used to filter the data to include only audit firms associated with the specific EU and EEA countries, as specified in configuration file `config/pull_data_cfg​`.
-This filtering step ensured that the analysis focuses on audit market concentration within the geographical scope and year range as defined by @EC_Report_2024.
+The data is pulled for the entire range 1972-2023 required for Task 1 and 2 to prevent double preparation step.
 
@@
 This project effectively demonstrates the use of a systematic and collaborative workflow for empirical accounting research, leveraging the TRR 266 Template for Reproducible Empirical Accounting Research.
-By following an open science approach, I successfully replicated key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency.
+By following an open science approach, I aimed to replicate key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency.
 While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process.

### 2025-01-31 doc/paper.qmd
change

@@
 **Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
+rrrr
 
@@
 qqq Comparing the replication results from Task 1&2 (see @ and @) with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
+
+```{python}
+#| label: fig-abnormal-r2
+#| fig-cap: "Replicated Figure 1: Abnormal Adjusted R² Values and Slope Coefficients from Annual Regressions"
+#| fig-align: center
+#| echo: false
+
+import pickle
+import matplotlib.pyplot as plt
+
+# Load the figure from the pickle file
+with open('../output/figure1_replication.pickle', 'rb') as f:
+    fig = pickle.load(f)
+
+# Render the figure explicitly
+plt.figure(fig.number)
+plt.show()
+```
 

### 2025-01-31 doc/paper.qmd
code enhance explanation

@@
 Data is pulled from WRDS using Python to integrate daily stock returns from CRSP (`crsp_a_stock.dsf`) with quarterly earnings announcement data from Compustat (`comp_na_daily_all.fundq`), linked via the Compustat-CRSP link table (`crsp_a_ccm.ccmxpf_lnkhist`).
-`permno` identifier matches stock returns to firm fundamentals via `gvkey` for exact firm/year match.
+`permno` unique identifier matches stock returns to firm fundamentals via `gvkey` for exact firm/year match.
 Key variables include `ret` (daily stock return) and `rdq` (earnings announcement date), enabling event study analysis from 1972 to 2023.
 While WRDS provides extensive financial datasets, documentation on precise variable selection and dataset integration is limited, requiring additional validation and cross-referencing with prior research.
-
 The data is pulled for the entire range 1972-2023 required for Task 1 and 2 to prevent double preparation step.
@@
 **Step 3: Analysis Implementation and Reproduction of Tables and Figure**
-rrrr
 

### 2025-01-31 code/python/pull_wrds_data.py

@@ -55,17 +55,18 @@ def get_wrds_login():
             'Please provide a WRDS password (it will not show as you type): ')
         return {'wrds_username': wrds_username, 'wrds_password': wrds_password}
 
-### LINKDATA Compustat/CRSP
 def pull_link_data(db):
-    log.info("Pulling link data Compustat/CRSP ...")
+    """
+    Pulls the linking table between Compustat and CRSP from WRDS.
+    """
     linkdata_df_wrds = db.get_table(library="crsp_a_ccm", table="ccmxpf_linktable")
     linkdata_df_wrds.to_parquet("data/pulled/linkdata_compustat_crsp.parquet")
     log.info("Pulling link data Compustat/CRSP... Done!")
 
-### CRSP DATA
 def pull_crsp_data(cfg, db):
-    log.info("Pulling CRSP data ...")
-    
+    """
+    Pulls daily stock return data from the CRSP database on WRDS.
+    """    
     # Prepare crsp_filter and crsp_vars
     crsp_vars = ', '.join(cfg['crsp_vars']) if cfg.get('crsp_vars') else "*"
     crsp_filter = ' AND '.join(cfg['crsp_filter']) if cfg.get('crsp_filter') else '1=1'
@@ -79,10 +80,10 @@ def pull_crsp_data(cfg, db):
 
     log.info("Pulling CRSP data ... Done!")
 
-### COMPUSTAT DATA
 def pull_compustat_data(cfg, db):
-    log.info("Pulling Compustat data ...")
-    
+    """
+    Pulls quarterly fundamental data from the Compustat database on WRDS.
+    """
     # Prepare fundq_filter and fundq_vars
     fundq_vars = ', '.join(cfg['fundq_vars']) if cfg.get('fundq_vars') else "*"
     fundq_filter = ' AND '.join(cfg['fundq_filter']) if cfg.get('fundq_filter') else '1=1'

### 2025-01-31 doc/paper.qmd
pap

@@
 **Step 2: Data Preparation**  
-The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021.
-To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.
+The merged dataset would integrate stock return data from CRSP (`crsp_daily_stock_returns`), firm fundamentals from Compustat (`compustat_fundq_1972_2023`), and the CRSP-Compustat linking table (`linkdata_compustat_crsp.parquet`).
+The `PERMNO` identifier from CRSP and `GVKEY` from Compustat are connected via `LPERMNO` in the linking table, ensuring correct firm-year alignment.
+Unnecessary variables from linked table, such as `linkprim`, `liid`, `linktype`, and `usedflag`, are dropped.
+The resulting dataset would retain only daily stock returns (`ret`), earnings announcement dates (`rdq`), fiscal year-end indicators (`fyr`), and firm identifiers (`permno, gvkey`), used further for BHR calculation and regression analysis.
 
-The `number_of_disclosed_pies` variable provides the clearest indication of statutory audits conducted by each auditor for PIEs.
-The definition of PIEs varies across EU and EEA countries [@AccountancyEurope_PIE_2017], but if Transparency Reports consistently follow country-specific definitions, using the provided variable is reasonable.
-An important verification step involved comparing the reported `number_of_disclosed_pies` with the count of unique `entity_map_fkey` entries for each `transparency_report_fkey`.
-This analysis revealed that 5,696 transparency reports included fewer entities in the dataset than the disclosed PIEs, suggesting that some PIE entities might be missing from the dataset.
-This discrepancy reflects missing PIE data rather than the inclusion of non-PIE entities, hence it is assumed that all entities in the dataset are PIEs, maintaining consistency in the framework for analysis.
-
-Additionally, missing values in key fields, including `transparency_report_fkey`, `entity_map_fkey`, `auditor_fkey`, and `trans_report_auditor_state`, were checked, and it was confirmed that no rows needed to be removed due to missing data, ensuring the completeness of the dataset.
-To focus on relevant data, rows with `number_of_disclosed_pies` equal to or less than zero were filtered, but no such rows were identified, and all observations were retained.
-
-Duplicate entries in the `entity_map_fkey` column were then analyzed, revealing 1,011 duplicate entities.
-I assume that duplicate entries in the dataset do not introduce significant issues for the replication of Figure 3.
-Duplicate entries for the same entity are expected in cases where an entity is audited by multiple audit firms or networks, potentially as part of a joint audit.
-Since these duplicates retain consistent information on `trans_report_auditor_state`, they do not distort country-level distributions.
-Additionally, while duplicates might expand representation across different auditor networks or groups, the essence of Figure 3 — focusing on aggregate distributions — remains unaffected.
-Therefore, these duplicates were not removed.
-
-Auditor network names were standardized to ensure consistency, with names like `|Mazars Worldwide|Praxity Global Alliance|` simplified to `|Mazars Worldwide|`, for example.
-This standardization helped avoid double-counting and unify same entries under consistent naming conventions.
-
-Audit firms were then categorized into groups, including the Big 4 (Deloitte, EY, KPMG, and PwC), the 10KAP (which includes the Big 4 along with other major networks listed in @sec-research_design_assumptions), 'Unaffiliated' firms (those outside the Big 4 and 10KAP).
-The `auditor_network` field contained 636 observations with missing values, which were grouped under the “Other (Blank)” category.
-I assume that these blank entries do not belong to the Big Four or 10KAP networks but may still contribute to the CR4 category in some countries.
-So, these entries were retained in the dataset and reviewed during the aggregation stage to validate their relevance.
-
-These preparation steps ensured alignment with the methodology of @EC_Report_2024 and the dataset’s readiness for subsequent analysis.
+After defining the event windows for each earnings announcement day in Q1-Q4, retain only the firms that have four earnings announcements per year, such that each of them falls within the same calendar year.
+Additionally, for the subgroup replication of Table 2 Panels C-D classify the firms based on their fiscal year-end (`fyr`) to define whether firms have December fiscal year-end firm or in any another month.
 

### 2025-01-31 doc/paper.qmd
new

@@
 **Step 2: Data Preparation**  
-The merged dataset would integrate stock return data from CRSP (`crsp_daily_stock_returns`), firm fundamentals from Compustat (`compustat_fundq_1972_2023`), and the CRSP-Compustat linking table (`linkdata_compustat_crsp.parquet`).
+Although not finished, the plan would be as follows: The merged dataset would integrate stock return data from CRSP (`crsp_daily_stock_returns`), firm fundamentals from Compustat (`compustat_fundq_1972_2023`), and the CRSP-Compustat linking table (`linkdata_compustat_crsp.parquet`).
 The `PERMNO` identifier from CRSP and `GVKEY` from Compustat are connected via `LPERMNO` in the linking table, ensuring correct firm-year alignment.
 Unnecessary variables from linked table, such as `linkprim`, `liid`, `linktype`, and `usedflag`, are dropped.
-The resulting dataset would retain only daily stock returns (`ret`), earnings announcement dates (`rdq`), fiscal year-end indicators (`fyr`), and firm identifiers (`permno, gvkey`), used further for BHR calculation and regression analysis.
+The resulting dataset would retain only daily stock returns (`ret`), earnings announcement dates (`rdq`), fiscal year-end indicators (`fyr`), and firm identifiers (`permno, gvkey`), used further for Buy-and-Hold Returns (BHR) calculation and regression analysis.
 
@@
 Additionally, for the subgroup replication of Table 2 Panels C-D classify the firms based on their fiscal year-end (`fyr`) to define whether firms have December fiscal year-end firm or in any another month.
+Control for the duplicate and missing firm/years.
 
 **Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
-The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data.
-The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021.
-For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts.
-The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.
+The analysis step computes the BHR returns and performs a cross-sectional regression for each distinct firm/year.
 
@@
 
-The following formula is used to calculate market share:
+The following formula is used to calculate calendar-year buy-and-hold returns, that measures the stock’s total performance over the year for each firm using daily CRSP returns:
 $$
-\text{Market Share (\%)} = \left( \frac{\text{Number of PIE Audits by Network Group}}{\text{Total PIE Audits in Country}} \right) \times 100
+BHR_{\text{annual}} = \prod_{t=1}^{T} (1 + R_t) - 1, \quad \text{where } R_t \text{ is the daily return and } T \text{ is the total trading days in a year.}
 $$
+
+Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as given below:
+$$
+BHR_{\text{annual}} = (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1, \quad \text{where } R_t \text{ is the daily return and } T \text{ is the total trading days in a year.}
+$$
+
+Next, perform cross-sectional regression for each firm/year - the main objective of @ball_how_2008's research:
+$$
+R_{\text{annual}} = \alpha_0 + \alpha_1 R_{\text{event}_1} + \alpha_2 R_{\text{event}_2} + \alpha_3 R_{\text{event}_3} + \alpha_4 R_{\text{event}_4} + \epsilon_i
+$$
+
+The DV (BHR_annual) is the firm’s calendar-year buy-and-hold return from CRSP, aggregated over all trading days, while the IVs (BHR_event) are the four quarterly earnings-announcement returns, computed as three-day buy-and-hold returns (-1, 0, +1) around each earnings announcement date (RDQ) from Compustat.
+Additionally, I compute abnormal  R^2 by benchmarking the adjusted  R^2  from annual regressions against the 4.8% baseline.
 

### 2025-01-31 doc/paper.qmd
paper

@@
 Since @ball_how_2008 do not explicitly describe their return computation, I compute Buy-and-Hold Returns (BHR) following the cumulative return formula as discussed in @gundersen_returns_2022.
-The BHR formula captures compounded returns over multiple days, reflecting the stock’s actual performance.
+The BHR formula captures compounded returns over multiple days, reflecting the stock’s actual performance, which is used to replicate Table 1.
 
@@
 Additionally, I compute abnormal  R^2 by benchmarking the adjusted  R^2  from annual regressions against the 4.8% baseline.
-
-The analysis also includes the creation of a bar chart visualizing market shares for all countries and the EU aggregate, saved in both PNG and pickle formats.
-The aggregated market share data is saved in CSV format, ensuring reproducibility and further analysis opportunities.
+This lays the ground for Table 2 replication.
 

### 2025-01-31 doc/paper.qmd
task 1 text

@@
 ## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
-Following @ball_how_2008, I focus the analysis on earnings announcements and stock returns from 1972 to 2006, ensuring that the data accurately reflects the original study’s methodology and findings.
-The replication aims to mirror the research design as closely as possible with the available data, maintaining consistency in sample selection, event window definitions, and return calculations.
+Following @ball_how_2008, I focus on earnings announcements and stock returns from 1972 to 2006, ensuring alignment with the original study’s methodology.
+This replication mirrors the research design, maintaining consistency in sample selection, event window definitions, and return calculations.
 
-Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication.
-Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.
+Based on the original paper, I do not gather analyst expectations or estimate earnings deviations, requiring only stock return data and earnings announcement dates, simplifying data collection.
 
-In addition, I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:
+To ensure clarity where @ball_how_2008 lacks explicit guidance, I impose the following assumptions:
 
-1.
-Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement.
-According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days.
-However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window.
-Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1).
-If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day.
-Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window.
+1.	Earnings announcement windows are defined as the three-day period surrounding the release (-1 to +1).
+According to @center_for_research_in_security_prices_crsp_crsp_2024 guide,since CRSP excludes weekends and holidays, if Day 0 falls on a non-trading day, it shifts to the next trading day.
+Similarly, Day -1 or +1 adjusts to the nearest available trading day.
 
-2.
-As in the original paper, firm-years are selected based on available stock return data in CRSP.
-While @ball_how_2008 restrict the sample to firms with at least 240 trading days per year, I follow the course guidance and do not apply this restriction, allowing for a slightly larger sample size.
-This adjustment should be considered when interpreting differences from the original study.
+2.	Firm-years are selected based on available CRSP stock return data.
+While @ball_how_2008 restricts the sample to firms with at least 240 trading days per year, I follow course guidance and do not impose this restriction, allowing for a slightly larger sample.
 
-3.
-Compustat includes both active and inactive firms, and the original study does not specify filtering based on firm activity.
-Thus, all firms meeting the sample selection criteria (i.e., four quarterly earnings announcements per year and available stock return data) are retained, regardless of their active status today.
+3.	Compustat includes active and inactive firms; since the original study does not filter based on firm activity, all firms meeting sample selection criteria (four quarterly earnings announcements per year, available stock returns) are retained.
 
-4.
-For historical analysis on securities, permanent identifiers, such as `PERMNO`, `PERMCO`, and `GVKEY` are used that never change for the duration of the company’s life span regardless of the name changes and are never being reused [@gow_empirical_2025].
-In this replication, variable `PERMNO` is used instead of `PERMCO` because it uniquely identifies individual securities rather than companies, ensuring that stock returns are accurately tracked at the security level.
-Since firms may have multiple share classes with distinct price movements, using `PERMNO` prevents aggregation issues that could arise with `PERMCO`, which groups all share classes under one identifier.
+4.	Permanent identifiers (`PERMNO`, `PERMCO`, `GVKEY`) ensure accurate historical tracking [@gow_empirical_2025].
+`PERMNO` is used instead of `PERMCO` as it uniquely identifies individual securities rather than companies, preventing aggregation issues from multiple share classes.
 
-5.
-The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually).
-Timing mismatches may arise, especially for firms with restated financials, leading to possible variations in event window alignment when calculating earnings-announcement returns.
-Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause differences in firm coverage or reported values.
+5.	The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database.
+As Compustat updates daily, while CRSP and CCM update annually, timing mismatches may arise.
+Unlike the original study, this replication uses the latest WRDS version as of January 2025, meaning database updates may introduce firm coverage or value differences.
 
@@
 ## Results {#sec-results1}
-Comparing the replication results of Figure 1 (see @fig-market-shares) with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
+Since Tables and Figure replication not finished, this section presents only the original @fig-fig1_original.
 
@@
 ```
-
-@fig-market-shares illustrates the... Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report.
-
-To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`.
-The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance.
-Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries.
-For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets.
-However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions.
-The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries.
-This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.
-
-The inclusion of additional audit networks through the 10KAP grouping increases the market share substantially across all countries, as expected.
-This is particularly evident in countries like Ireland, Malta, and the Netherlands, where the 10KAP share reaches 100%, reflecting the full inclusion of statutory audits under this grouping.
-In contrast, countries like Bulgaria and Poland, with 10KAP shares of 41.8% and 63.6%, respectively, suggest the presence of a substantial number of statutory audits conducted by unaffiliated or smaller firms.
-
-In the analysis of CR4 market shares, I verified whether the four largest audit firms (CR4) in each country overlapped entirely with the Big 4 audit firms.
-This overlap occurred in 15 out of 28 countries, where CR4 and Big 4 market shares were identical.
-In the remaining 13 countries, at least one non-Big 4 firm contributed significantly to the statutory audits, resulting in distinct CR4 market shares.
-These findings align with @EC_Report_2024, which notes that in 13 Member States, the Big Four are not the four largest audit firms in terms of the total number of PIE statutory audit opinions.
-This highlights the gradual diversification in the audit market in some countries, where non-Big 4 firms are playing a more prominent role, while the Big 4 continue to dominate in others.
-
-At the EU level, the aggregated market shares further underscore the dominance of these major players.
-The Big 4 account for 70% of statutory audits, compared to @EC_Report_2024, which notes an average EU market share of 59% for the Big 4 in 2021, down from 70% in 2018.
-The broader 10KAP grouping in my output reaches nearly 90%, exceeding the 81% reported by @EC_Report_2024.
-The CR4 market share at the EU level also stands at 70%, aligning with the Big 4, and is consistent with the average CR4 market share reported by @EC_Report_2024.
-These results highlight the varying degrees of market concentration across Europe, with certain countries demonstrating a highly centralized audit market dominated by the Big 4, while others display a more distributed market landscape, incorporating both major and smaller audit firms.
-The slight discrepancies in the figures suggest potential differences in methodologies, data coverage, or sample definitions.
-
-Based on the results for Austria, the Big 4 market share is 86.7% in my analysis, aligning closely with the approximate 85% represented in bar chart of @EC_Report_2024.
-Similarly, the 10KAP market share of 92.55% in my analysis corresponds well with the slightly higher bar in the report, and the CR4 market share of 86.7% aligns perfectly with the Big 4 share, confirming the dominance of these firms in Austria’s audit market.
-This consistency highlights the robustness of the replicated analysis for this country.
-
-The results for Romania show notable discrepancies.
-The EC Report indicates market shares of 15% for the Big 4, 16% for CR4, and 24% for 10KAP, while my analysis reports significantly higher values: 63%, 70.61%, and 78.38%, respectively.
-These differences likely arise from assumptions made in @sec-research_design_assumptions like variations in PIE definitions and auditor classifications.
-The report by @EC_Report_2024 may use stricter criteria, reflecting Romania’s decentralized market where non-Big 4 firms dominate, unlike the broader inclusion in my dataset.
-
-In summary, the replication effectively captures the original report's key findings, confirming the dominance of the Big 4 and the broader 10KAP group in the European audit market.
-The analysis highlights varying degrees of market concentration across countries, with some demonstrating a more decentralized audit landscape.
-While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.
-qqq we confirm?
-"The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market.
-By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system.
-The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons.
-By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking.
-Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."
 
@@
 
+qqq we confirm?
+"The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market.
+By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system.
+The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons.
+By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking.
+Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."
+
 # Task 4 - Research Design for a Non-Archival Study {#sec-task4}

### 2025-01-31 doc/paper.qmd
task 2

@@
 ## Replication Steps {#sec-replication_steps2}
+The pull, preparation, and analysis step would remain the same as designed in @sec-replication_steps1 with the only change in data range.
+
 ## Results {#sec-results2}
+The sample shift to 2007–2023 is expected to bring potential shifts in earnings announcement informativeness due to significant economic and regulatory events.
+The 2008 Global Financial Crisis likely disrupted earnings predictability, with heightened volatility and uncertainty increasing the market’s sensitivity to earnings reports.
+The COVID-19 pandemic 2020 introduced extreme market uncertainty, potentially amplifying the informativeness of earnings announcements as investors relied on them to gauge firm resilience and recovery.
+Additionally, the introduction of Regulation (EU) No 537/2014 may have influenced earnings informativeness by improving transparency, audit quality, and financial reporting compliance across EU countries.
+Differences in compliance and audit coverage could have led to variations in how earnings announcements reflect new information in stock prices, potentially contributing to cross-country disparities in earnings informativeness.
 

### 2025-01-31 doc/paper.qmd
task 1 text

@@
 # Task 3 - Cross-Country Replication {#sec-task3}
-Task 3 extends the analysis beyond the United States by replicating Figure 1 using 1972-2023 data (if entire data range pull possible) from a non-U.S.
-market, providing insights into how earnings informativeness varies across different regulatory environments and market structures.
-This task requires mapping variables from CRSP/Compustat to their equivalents in Worldscope/Datastream, adjusting for differences in accounting standards, market liquidity, and institutional factors.
-Worldscope (Thomson/Refinitiv) serves as the international alternative of Compustat for earnings announcement data, while Datastream provides stock market data for non-U.S.
-companies.
-While the core replication methodology remains the same, careful data handling and economic interpretation are crucial to account for cross-country analysis with Canada.
+Task 3 extends the analysis beyond the U.S.
+by replicating Figure 1 using 1972–2023 data from a non-U.S.
+market, examining how earnings informativeness varies across regulatory environments and market structures.
+This requires mapping CRSP/Compustat variables to their Worldscope/Datastream equivalents while adjusting for accounting standards, market liquidity, and institutional factors.
+Worldscope provides earnings announcement data, and Datastream covers stock returns.
+While the core methodology remains, careful data handling and interpretation are essential for cross-country analysis, particularly with Canada.
 
@@
 
-Canada as the country of choice was influenced by the alignment with the methodology of @ball_how_2008, where the key factor in the selection was the availability of quarterly earnings reports, which ensures comparability with U.S.
-data.
-For Canada, the reporting frequency is majority 4x, with some 2x, similar to the US [@short_short_2025].
-While Canada has a smaller market size than the U.S., its regulatory environment, reporting frequency, and institutional settings are highly comparable, making it an optimal choice for the non-U.S.
-analysis.
-Additionally, Canada features a developed capital market with high trading volume and liquidity, ensuring that stock price reactions to earnings announcements are observable in the replication.
-A further advantage is that Canadian firms registered with the U.S.
-Securities and Exchange Commission (SEC) can report under U.S.
+Canada was chosen for its quarterly reporting frequency, ensuring comparability with U.S.
+data, as most firms report four times per year, with some semi-annual reports [@short_short_2025].
+Despite its smaller market size, Canada’s regulatory environment, liquidity, and institutional settings closely align with the U.S., making it an ideal candidate.
+Additionally, Canadian firms registered with the SEC can report under U.S.
 GAAP, making their financial disclosures fully compatible with U.S.
 firms.
-This reduces methodological differences to the original study.
 
@@
 Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets demands modular approach.
-Therefore, I isolate the workflow for @sec-task3 into working files `...-wscp`, thus reducing complicated dependencies across tasks.
 
@@
 I verified whether Worldscope and Datastream follow the same earnings announcement date convention as Compustat or if they report earnings based on fiscal periods.
-I decided to use Worldscope items 5901–5904 from historical stock-related data in `wrds_ws_stock`, which represent the actual date when a company publicly reports its earnings for each quarter, where, however, data for these fields is generally not available prior to 1992.
-[@thomson_financial_worldscope_2007, p.281].
+I decided to use Worldscope items 5901–5904 from historical stock-related data in `wrds_ws_stock`, which represent the actual date when a company publicly reports its earnings for each quarter, where, however, data for these fields is generally not available prior to 1992 [@thomson_financial_worldscope_2007, p.281].
 This may cause limited data sample size.
@@
 
-5. Similar to @sec-task1, I use returns `ret` variable in Datastream to simplify the process, presented as percentage change. Bid and ask prices are ignored.
+5. Similar to @sec-task1, I use returns `ret` variable in Datastream for returns, presented as percentage change. Bid and ask prices are ignored.
 
@@
 ## Replication Steps {#sec-replication_steps3}
-Same as in @sec-task1 the analysis involves gathering and filtering stock return and earnings announcement data, linking Datastream stock data with WSCP (Worldscope), and estimating the relationship between annual returns and earnings-announcement window returns.
-The replication process follows a structured workflow of data pull, preparation, and analysis, ensuring consistency with the original study.
+The process is same as in @sec-task1.
 
@@
 
-The data pull step retrieves quarterly earnings announcement dates from Worldscope and daily stock returns from Datastream, filtering for Canadian firms from 1980 onward.
+Next, retrieve quarterly earnings announcement dates from Worldscope and daily stock returns from Datastream, filtering for Canadian firms from 1980 onward.
 The datasets are saved separately and later merged using firm-level identifiers.
@@
 Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year.
-The final dataset consists of only 616,980 valid firm-year observations, starting in 1996 only, signaling the potential difference in the accounting reporting standards between the U.S.
-and Canada.
+Furthermore, I extend dynamically shift the missing values for trading days -1,0,1 within 3 day window, due to small sample size to keep more earning announcemnet windows.
 
+From this cleaned dataset, BHR event returns are computed.
+Then, annual stock returns for the firms of the filtered sample are extracted from Datastream pulled data .
+Finally, the Annual BHR Returns are calculated.
 Notably, after pulling the annual stock data for further annual return calculation, all infocodes present an average of 250 trading days, highlighting full year stock coverage.
@@
 **Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
+I conduct the earnings informativeness analysis by computing summary statistics (Table 1), running annual regressions (Table 2), and generating a replication of Figure 1.
+First, I loaded the computed event-window and annual buy-and-hold returns (BHR_3day, BHR_Annual) and produced summary statistics similar to @ball_how_2008.
+Next, I performed annual cross-sectional regressions of stock returns on earnings-announcement returns, benchmarking against an Abnormal R² (adjusted R² minus 4.8%), while handling missing data and ensuring a valid number of observations per year.
+Finally, the script plots Figure 1, visualizing Abnormal R² trends (Panel A) and slope coefficients (Panel B) over time, saving it as both a PNG and a pickle file for further use.
 

### 2025-01-31 doc/paper.qmd
step 3

@@
 Comparing the replication results with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
+The original figure shows a general upward trend in abnormal  R^2 , peaking in the early 2000s, whereas the replicated figure captures greater volatility in the later years (2010–2023).
+Additionally, Ball’s figure suggests a smoother long-term dynamic, while the replication exhibits more pronounced fluctuations, particularly post-2010.
+Panel B in replicated figure exhibits higher volatility and larger coefficient magnitudes, suggesting increased earnings informativeness post-2006, while Ball’s original figure has more stable and lower-magnitude coefficients.
 
-qqq Comparing the replication results from Task 1&2 (see @ and @) with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
+The post-2000 period in the replication shows more inconsistent abnormal  R^2  values, possibly reflecting evolving market structures, shifts in disclosure practices, and increased earnings informativeness following regulatory changes (e.g., IFRS adoption, post-SOX adjustments, different financial market structure).
+The pronounced fluctuations could also be driven by global financial crisis, Canada's higher market concentration, fewer publicly traded firms, and potential regulatory differences, which may affect earnings informativeness and stock return patterns.
+The variability in slope coefficients further suggests that earnings announcements’ impact on stock returns is less stable than in prior decades, potentially due to differences in investor response.
 
@@
 ```
-
-qqq we confirm?
-"The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market.
-By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system.
-The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons.
-By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking.
-Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."
 

### 2025-01-31 doc/paper.qmd
final paper

@@
 By following an open science approach, I aimed to replicate key tables and figures from @ball_how_2008, providing insights into how earnings announcements contribute to price formation and market efficiency.
-While exact replications often yield different samples and outcomes due to dataset updates or methodological variations, my results align closely with the statistics presented in the original study, reinforcing the reliability of the replication process.
-Moreover, by extending the analysis beyond the original study’s U.S.
+By extending the analysis beyond the original study’s U.S.
 market focus, the project highlights how market structures and investor behaviors influence the informativeness of earnings disclosures in different jurisdictions.

### 2025-01-31 doc/paper.qmd
paper final

@@
     lof: true  # Enables List of Figures
-    lot: true  # Enables List of Tables
+    lot: false  # Disables List of Tables
 fig_caption: yes
@@
 **Step 1: Pulling the Data and Managing the Databases**  
-Data is pulled from WRDS using Python to integrate daily stock returns from CRSP (`crsp_a_stock.dsf`) with quarterly earnings announcement data from Compustat (`comp_na_daily_all.fundq`), linked via the Compustat-CRSP link table (`crsp_a_ccm.ccmxpf_lnkhist`).
+Data is pulled from WRDS using Python to integrate daily stock returns from CRSP (`crsp_a_stock.dsf`) with quarterly earnings announcement data from Compustat  
+(`comp_na_daily_all.fundq`), linked via the Compustat-CRSP link table  
+(`crsp_a_ccm.ccmxpf_lnkhist`).
 `permno` unique identifier matches stock returns to firm fundamentals via `gvkey` for exact firm/year match.
@@
 $$
-BHR_{\text{annual}} = (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1, \quad \text{where } R_t \text{ is the daily return and } T \text{ is the total trading days in a year.}
+\begin{aligned}
+BHR_{\text{event}} &= (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1
+\\
+\text{where } R_t & \text{ is the daily return and } T \text{ is the total trading days in a year.}
+\end{aligned}
 $$
@@
 $$
-R_{\text{annual}} = \alpha_0 + \alpha_1 R_{\text{event}_1} + \alpha_2 R_{\text{event}_2} + \alpha_3 R_{\text{event}_3} + \alpha_4 R_{\text{event}_4} + \epsilon_i
+R_i(\text{annual}) = a_0 + a_1 R_i(\text{window1}) + a_2 R_i(\text{window2}) + a_3 R_i(\text{window3}) + a_4 R_i(\text{window4}) + \varepsilon_i
 $$
@@
 Comparing the replication results with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.
-The original figure shows a general upward trend in abnormal  R^2 , peaking in the early 2000s, whereas the replicated figure captures greater volatility in the later years (2010–2023).
+The original figure shows a general upward trend in abnormal  R² , peaking in the early 2000s, whereas the replicated figure captures greater volatility in the later years (2010–2023).
 Additionally, Ball’s figure suggests a smoother long-term dynamic, while the replication exhibits more pronounced fluctuations, particularly post-2010.

### 2025-01-31 code/python/do_analysis.py
clean up

@@ -1,276 +1,0 @@
-# We start by loading the libraries that we will use in this analysis.
-import os
-import pickle
-import pandas as pd
-import matplotlib.pyplot as plt
-from utils import read_config, setup_logging
-
-# Set up logging
-log = setup_logging()
-
-def main():
-    log.info("Performing main analysis...")
-    
-    # Load the configuration file
-    cfg = read_config('config/do_analysis_cfg.yaml')
-    
-    # Load the prepared transparency data using the path from the config file
-    prepared_data = load_data(cfg['prepared_data_save_path'])
-    
-    # Calculate market shares for each group
-    big4_shares = calculate_big4_market_share(prepared_data)
-    kap10_shares = calculate_kap10_market_share(prepared_data)
-    cr4_shares = calculate_cr4_market_share(prepared_data, big4_shares)  # Pass big4_shares as an argument
-    eu_shares = calculate_eu_level_market_shares(prepared_data)
-    
-    # Combine results into one DataFrame
-    market_shares = combine_market_shares(big4_shares, kap10_shares, cr4_shares, eu_shares)
-    
-    # Save the aggregated market shares to a CSV file
-    save_market_shares(market_shares, cfg['aggregated_data_save_path'])
-
-    # Plot the results
-    plot_market_shares(market_shares, cfg['figure_save_path'], cfg['pickle_save_path'])
-    
-    log.info("Performing main analysis and plotting...Done!")
-
-def load_data(data_path):
-    """
-    Load the prepared transparency data from the specified path.
-    """
-    df = pd.read_csv(data_path)
-    return df
-
-def calculate_big4_market_share(df):
-    """
-    Calculate market share for Big 4 by country.
-    """
-    # Step 1: Calculate total PIE audits by counting rows per country
-    country_totals = df.groupby('trans_report_auditor_state').size().reset_index(name='total_pie_audits')
-    print("Country Totals (All Audits):")
-    print(country_totals.head(9))
-    
-    # Step 2: Filter data for Big 4
-    big4_df = df[df['network_group'] == 'Big 4']
-    print("Filtered Big 4 Data:")
-    print(big4_df.head())
-    
-    # Step 3: Calculate Big 4 PIE audits by counting rows per country
[…]

### 2025-01-31 code/python/prepare_data.py

@@ -1,185 +1,0 @@
-# --- Header -------------------------------------------------------------------
-# Prepare the pulled data for further analysis as per the requirements by EC Report (2024)
-#
-# (C) Melisa Mazaeva - See LICENSE file for details
-# ------------------------------------------------------------------------------
-
-import pandas as pd
-from utils import read_config, setup_logging
-
-log = setup_logging()
-def main():
-    log.info("Preparing data for analysis ...")
-    cfg = read_config('config/prepare_data_cfg.yaml')
-
-    # Load the pulled data
-    transparency_data = pd.read_csv(cfg['audit_analytics_save_path'])
-    initial_obs_count = len(transparency_data)
-    log.info(f"Initial number of observations after pulling data: {initial_obs_count}")
-
-    # Standardize Greece abbreviation
-    transparency_data = standardize_greece_abbreviation(transparency_data)
-
-    # Verify disclosed PIEs alignment with listed entities
-    transparency_data = verify_disclosed_pies_alignment(transparency_data)
-
-    # Check and handle blank values in vital fields
-    vital_fields = ['transparency_report_fkey', 'entity_map_fkey', 'auditor_fkey', 'trans_report_auditor_state']
-    transparency_data = check_and_handle_blanks(transparency_data, vital_fields)
-
-    # Ensure rows with NUMBER_OF_DISCLOSED_PIES > 0
-    transparency_data = filter_disclosed_pies(transparency_data)
-
-    # Check for duplicates in entity_map_fkey
-    check_for_joint_audits(transparency_data)
-
-    # Handle missing Auditor Network values
-    transparency_data['auditor_network'] = transparency_data['auditor_network'].fillna('Other (Blank)')
-    missing_networks = transparency_data['auditor_network'].value_counts().get('Other (Blank)', 0)
-    log.info(f"Number of observations with missing Auditor Network: {missing_networks}")
-
-    # Map duplicate auditor networks to standardized names
-    transparency_data = standardize_auditor_network_names(transparency_data)
-
-    # Map auditor networks into groups
-    transparency_data = map_auditor_networks(transparency_data)
-
-    # Save the prepared dataset
-    transparency_data.to_csv(cfg['prepared_data_save_path'], index=False)
-    log.info(f"Prepared data saved to {cfg['prepared_data_save_path']}")
-
-    log.info("Preparing data for analysis ... Done!")
-
[…]

### 2025-03-08 doc/paper.qmd
commit

@@
 author:
-  - name: Melisa Mazaeva
-    email: melisa.mazaeva@student.hu-berlin.de
+  - name: Mel Mzv
+    email: m@student.hu-berlin.de
     affiliations:

### 2025-03-08 code/python/prepare_data-wscp.py

@@ -1,7 +1,7 @@
 # --- Header -------------------------------------------------------------------
 # Prepare the pulled data for further analysis as per Task 3 requirements
 #
-# (C) Melisa Mazaeva - See LICENSE file for details
+# (C) Mel Mzv - See LICENSE file for details
 # ------------------------------------------------------------------------------
 
 import pandas as pd
